---
title: "Models"
bibliography: references.bib
date: "Last compiled on `r format(Sys.time(), '%B, %Y')`"
output: 
  html_document:
    css: tweaks.css
    toc:  true
    toc_float: true
    number_sections: false
    toc_depth: 1
    code_folding: show
    code_download: yes
---

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test3"))
options(width = 100)
rgl::setupKnitr()
```


```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```


---  

# Getting started

To copy the code, click the button in the upper right corner of the code-chunks.

## clean up

```{r, results='hide'}
rm(list=ls())
gc()
```

<br>

## general custom functions

- `fpackage.check`: Check if packages are installed (and install if not) in R
- `fsave`: Function to save data with time stamp in correct directory
- `fload`: Function to load R-objects under new names

```{r}
fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

fsave <- function(x, file, location = "./data/processed/", ...) {
    if (!dir.exists(location))
        dir.create(location)
    datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
    totalname <- paste(location, datename, file, sep = "")
    print(paste("SAVED: ", totalname, sep = ""))
    save(x, file = totalname)
}


fload  <- function(fileName){
  load(fileName)
  get(ls()[ls() != "fileName"])
}

colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }
```

<br>

## necessary packages

- `tidyverse`
- `ggplot2`
- `reshape2`
- `lattice`

```{r, echo=FALSE, warning=FALSE, results='hide'}
packages = c("tidyverse", "ggplot2", "reshape2", "lattice")
fpackage.check(packages)
rm(packages)
```

<br>

## import data

Load in the created data-set. You may have to adjust the date..

```{r,eval=F}
today <- substr(gsub("[:-]", "", Sys.Date()-1), 1, 8)
#today <- substr(gsub("[:-]", "", Sys.Date()), 1, 8)
data <- fload(paste0("./data/processed/", today, "output.R"))
```

<br>

## reshape 

```{r,eval=F}
#add multiplexity as a control 
#subtract by 1 to reach meaningful intercept (i.e., monoplex)
data$multiplexity <- rowSums(cbind(data$cdn, data$study, data$bff, data$csn)) - 1

#also add as dummies
#data$monoplex <- ifelse(data$multiplexity==0,1,0)
#data$multiplex <- ifelse(data$multiplexity>0,1,0)

#for now, get only monoplex ties
data.1 <- data[which(data$multiplexity==0),]

# Reshape the data from wide to long format
df_long <- data.1 %>% pivot_longer(which(grepl("accuracy", names(data.1))), names_to = "item", values_to = "accuracy")
df_long$respnr <- factor(df_long$respnr, ordered = FALSE)
```


----

<br>

# OLS

```{r,eval=F}
mod1 <- lm(accuracy ~ cdn + study + bff, data=df_long)
summary(mod1)

```


# Mixed effects model

we have individual responses (ego and alter: L1), nested within dyads (L2).

<br>

## null model

No predictors

```{r,eval=F}
mod1 <- lmer(accuracy ~ (1|respnr), data=df_long, REML=FALSE)
summary(mod1)

?lmer
df_long$value




df_long$respnr <- factor(df_long$respnr, ordered = FALSE)
mod1 <- lmer(value ~ (1|respnr), data=df_long)
#summary(mod1)

df_long %>%
  #save predicted values
  mutate(pred_accuracy = fitted(mod1)) %>%
  #graph
  ggplot(aes(x=Relationship, y=pred_accuracy, group=respnr, color=respnr)) + theme_classic() +
  geom_point(size=1) -> p

p <- p + labs(x = "Relationship type", y = "Predicted accuracy score (0-1)", title = "Predicted values of null-model (mod1).", subtitle = "Predicted values per (monoplex) relationship type.")
p <- p + theme(legend.position = "none")
print(p)
```


## Random intercept

add independent variable, embeddedness

```{r,eval=F}
# embeddedness
mod2 <- lmer(value ~ Relationship + (1|respnr), data=df_long)
#summary(mod2)

df_long %>%
  #save predicted values
  mutate(pred_accuracy = fitted(mod2)) %>%
  #graph
  ggplot(aes(x=Relationship, y=pred_accuracy, group=respnr, color=respnr)) + theme_classic() +
  geom_point(size=1) -> p

p <- p + labs(x = "Relationship type", y = "Predicted accuracy score (0-1)", title = "Predicted values of random intercept model (mod2).", subtitle= "Ego-level random intercept. Predicted values per (monoplex) relationship type.")
p <- p + theme(legend.position = "none")
print(p)
```

<br>

also add embeddedness

```{r,eval=F}
# embeddedness
mod3 <- lmer(value ~ Relationship + embeddedness + (1|respnr), data=df_long)
#summary(mod3)

df_long %>%
  #save predicted values
  mutate(pred_accuracy = fitted(mod3)) %>%
  #graph
  ggplot(aes(x=Relationship, y=pred_accuracy, group=respnr, color=respnr)) + theme_classic() +
  geom_point(size=1) -> p

p <- p + labs(x = "Relationship type", y = "Predicted accuracy score (0-1)", title = "Predicted values of random intercept model (mod3).", subtitle= "Ego-level random intercept. Predicted values per (monoplex) relationship type.")
p <- p + theme(legend.position = "none")
print(p)
```

<br>

Note: model with random slope is near singular..




