---
title: "Descriptives"
bibliography: references.bib
date: "Last compiled on `r format(Sys.time(), '%B, %Y')`"
output: 
  html_document:
    css: tweaks.css
    toc:  true
    toc_float: true
    number_sections: false
    toc_depth: 1
    code_folding: show
    code_download: yes
---

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test3"))
options(width = 100)
rgl::setupKnitr()
```


```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```


---  

# Getting started

To copy the code, click the button in the upper right corner of the code-chunks.

## clean up

```{r, results='hide'}
rm(list=ls())
gc()
```

<br>

## general custom functions

- `fpackage.check`: Check if packages are installed (and install if not) in R
- `fsave`: Function to save data with time stamp in correct directory
- `fload`: Function to load R-objects under new names
- `flegend`: add common legend to combined ggplot2 ([source](https://www.geeksforgeeks.org/add-common-legend-to-combined-ggplot2-plots-in-r/)).


```{r}
fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

fsave <- function(x, file, location = "./data/processed/", ...) {
    if (!dir.exists(location))
        dir.create(location)
    datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
    totalname <- paste(location, datename, file, sep = "")
    print(paste("SAVED: ", totalname, sep = ""))
    save(x, file = totalname)
}


fload  <- function(fileName){
  load(fileName)
  get(ls()[ls() != "fileName"])
}

flegend <- function(plot) {
	
# get tabular interpretation of plot
plot_table <- ggplot_gtable(ggplot_build(plot))
	
# Mark only legend in plot
legend_plot <- which(sapply(plot_table$grobs, function(x) x$name) == "guide-box")
							
# extract legend
legend <- plot_table$grobs[[legend_plot]]
							
# return legend
return(legend)
}


colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }
```

<br>

## necessary packages

- `tidyverse`
- `ggplot2`
- `reshape2`
- `lattice`
- `RColorBrewer`

```{r, warning=FALSE, results='hide'}
packages = c("tidyverse", "ggplot2", "reshape2", "lattice", "RColorBrewer")
fpackage.check(packages)
rm(packages)
```

<br>

## import data

Load in the replicated data-set. You may have to adjust the date...

You may also obtain it by downloading: `r xfun::embed_file("./data shared/output.RDa")`


```{r}
#today <- substr(gsub("[:-]", "", Sys.time()), 1, 8) #get todays date
today <- "20230511" 
data <- fload(paste0("./data/processed/", today, "output.RDa"))
```


```{r,eval=F}
#145 unique (ego-) respondents
length(unique(data$respnr))

#235 responses from ego (about alters), 235 responses from alter (about ego)
table(data$ego)
```


<br>


Let's for now focus only on mono-plex ties, that is alters that were listed in one name generator only.

```{r}
data$multiplexity <- rowSums(cbind(data$cdn, data$study, data$bff, data$csn))
#prop.table(table(data$multiplexity))[1]*100

data.1 <- data[which(data$multiplexity==1), ]
#328 monoplex ties

#make a character variable indicating the type of (monoplex) relation
data.1$Relationship <- ifelse(data.1$cdn==1, "Confidant", ifelse(data.1$study==1, "Study partner", ifelse(data.1$bff==1, "Best Friend", ifelse(data.1$csn==1, "Sports partner", NA) )))
```

<br>

`r round(prop.table(table(data$multiplexity))[1]*100)` % of relations in our data-set are monoplex.

<br>


# Relationship type

Does accuracy of estimating an alter's behavior/attitude depend on the type of relationship?


We use three measures of accuracy:

- continuous accuracy measure, abs(perception - truth) / range(item) (`accuracy`)

two additional: 

- dichotomous: does the perception and the self-report/truth fall on the same side of the midpoint of the scale? (`accuracy_side`)
- dichotomous: does the perception precisely match the self-report/truth? (`accuracy_precise`)

```{r}
#accuracy side
data.1$LR.accuracy_side <- ifelse(( (data.1$LR.perception %in% c(0:10)[1:round(length(c(0:10))/2)] & data.1$LR.truth %in% c(0:10)[1:round(length(c(0:10))/2)])
                                    |(data.1$LR.perception %in% c(0:10)[round(length(c(0:10))/2):11] & data.1$LR.truth %in%
                                        c(0:10)[round(length(c(0:10))/2):11]) ) ,1,0)

data.1$cap.accuracy_side <- ifelse( (data.1$cap.perception %in% c(1:4)[1:(length(1:4)/2)] & data.1$cap.truth %in% c(1:4)[1:(length(1:4)/2)] ) | 
  (data.1$cap.perception %in% c(1:4)[((length(1:4)/2)+1):4] & data.1$cap.truth %in% c(1:4)[((length(1:4)/2)+1):4]), 1, 0)
data.1$fly.accuracy_side <- ifelse( (data.1$fly.perception %in% c(1:4)[1:(length(1:4)/2)] & data.1$fly.truth %in% c(1:4)[1:(length(1:4)/2)] ) | 
  (data.1$fly.perception %in% c(1:4)[((length(1:4)/2)+1):4] & data.1$fly.truth %in% c(1:4)[((length(1:4)/2)+1):4]), 1, 0)
data.1$meat.accuracy_side <- ifelse( (data.1$meat.perception %in% c(1:4)[1:(length(1:4)/2)] & data.1$meat.truth %in% c(1:4)[1:(length(1:4)/2)] ) | 
  (data.1$meat.perception %in% c(1:4)[((length(1:4)/2)+1):4] & data.1$meat.truth %in% c(1:4)[((length(1:4)/2)+1):4]), 1, 0)
data.1$animal.accuracy_side <- ifelse( (data.1$animal.perception %in% c(1:4)[1:(length(1:4)/2)] & data.1$animal.truth %in% c(1:4)[1:(length(1:4)/2)] ) | 
  (data.1$animal.perception %in% c(1:4)[((length(1:4)/2)+1):4] & data.1$animal.truth %in% c(1:4)[((length(1:4)/2)+1):4]), 1, 0)
data.1$nature.accuracy_side <- ifelse( (data.1$nature.perception %in% c(1:4)[1:(length(1:4)/2)] & data.1$nature.truth %in% c(1:4)[1:(length(1:4)/2)] ) | 
  (data.1$nature.perception %in% c(1:4)[((length(1:4)/2)+1):4] & data.1$nature.truth %in% c(1:4)[((length(1:4)/2)+1):4]), 1, 0)
data.1$replace.accuracy_side <- ifelse( (data.1$replace.perception %in% c(1:4)[1:(length(1:4)/2)] & data.1$replace.truth %in% c(1:4)[1:(length(1:4)/2)] ) | 
  (data.1$replace.perception %in% c(1:4)[((length(1:4)/2)+1):4] & data.1$replace.truth %in% c(1:4)[((length(1:4)/2)+1):4]), 1, 0)
data.1$student.accuracy_side <- ifelse( (data.1$student.perception %in% c(1:4)[1:(length(1:4)/2)] & data.1$student.truth %in% c(1:4)[1:(length(1:4)/2)] ) | 
  (data.1$student.perception %in% c(1:4)[((length(1:4)/2)+1):4] & data.1$student.truth %in% c(1:4)[((length(1:4)/2)+1):4]), 1, 0)
data.1$threat.accuracy_side <- ifelse( (data.1$threat.perception %in% c(1:4)[1:(length(1:4)/2)] & data.1$threat.truth %in% c(1:4)[1:(length(1:4)/2)] ) | 
  (data.1$threat.perception %in% c(1:4)[((length(1:4)/2)+1):4] & data.1$threat.truth %in% c(1:4)[((length(1:4)/2)+1):4]), 1, 0)
data.1$sechand.accuracy_side <- ifelse( (data.1$sechand.perception %in% c(1:4)[1:(length(1:4)/2)] & data.1$sechand.truth %in% c(1:4)[1:(length(1:4)/2)] ) | 
  (data.1$sechand.perception %in% c(1:4)[((length(1:4)/2)+1):4] & data.1$sechand.truth %in% c(1:4)[((length(1:4)/2)+1):4]), 1, 0)
data.1$imp_crime.accuracy_side <- ifelse( (data.1$imp_crime.perception %in% c(1:4)[1:(length(1:4)/2)] & data.1$imp_crime.truth %in% c(1:4)[1:(length(1:4)/2)] ) | 
  (data.1$imp_crime.perception %in% c(1:4)[((length(1:4)/2)+1):4] & data.1$imp_crime.truth %in% c(1:4)[((length(1:4)/2)+1):4]), 1, 0)
data.1$imp_discrim.accuracy_side <- ifelse( (data.1$imp_discrim.perception %in% c(1:4)[1:(length(1:4)/2)] & data.1$imp_discrim.truth %in% c(1:4)[1:(length(1:4)/2)] ) | 
  (data.1$imp_discrim.perception %in% c(1:4)[((length(1:4)/2)+1):4] & data.1$imp_discrim.truth %in% c(1:4)[((length(1:4)/2)+1):4]), 1, 0)
data.1$imp_housing.accuracy_side <- ifelse( (data.1$imp_housing.perception %in% c(1:4)[1:(length(1:4)/2)] & data.1$imp_housing.truth %in% c(1:4)[1:(length(1:4)/2)] ) | 
  (data.1$imp_housing.perception %in% c(1:4)[((length(1:4)/2)+1):4] & data.1$imp_housing.truth %in% c(1:4)[((length(1:4)/2)+1):4]), 1, 0)
data.1$imp_refugee.accuracy_side <- ifelse( (data.1$imp_refugee.perception %in% c(1:4)[1:(length(1:4)/2)] & data.1$imp_refugee.truth %in% c(1:4)[1:(length(1:4)/2)] ) | 
  (data.1$imp_refugee.perception %in% c(1:4)[((length(1:4)/2)+1):4] & data.1$imp_refugee.truth %in% c(1:4)[((length(1:4)/2)+1):4]), 1, 0)
data.1$imp_climate.accuracy_side <- ifelse( (data.1$imp_climate.perception %in% c(1:4)[1:(length(1:4)/2)] & data.1$imp_climate.truth %in% c(1:4)[1:(length(1:4)/2)] ) | 
  (data.1$imp_climate.perception %in% c(1:4)[((length(1:4)/2)+1):4] & data.1$imp_climate.truth %in% c(1:4)[((length(1:4)/2)+1):4]), 1, 0)


#accuracy precise
data.1$LR.accuracy_precise <- ifelse(data.1$LR.perception == data.1$LR.truth,1,0)
data.1$cap.accuracy_precise <- ifelse(data.1$cap.perception == data.1$cap.truth,1,0)
data.1$fly.accuracy_precise <- ifelse(data.1$fly.perception == data.1$fly.truth,1,0)
data.1$meat.accuracy_precise <- ifelse(data.1$meat.perception == data.1$meat.truth,1,0)
data.1$animal.accuracy_precise <- ifelse(data.1$animal.perception == data.1$animal.truth,1,0)
data.1$nature.accuracy_precise <- ifelse(data.1$nature.perception == data.1$nature.truth,1,0)
data.1$replace.accuracy_precise <- ifelse(data.1$replace.perception == data.1$replace.truth,1,0)
data.1$student.accuracy_precise <- ifelse(data.1$student.perception == data.1$student.truth,1,0)
data.1$threat.accuracy_precise <- ifelse(data.1$threat.perception == data.1$threat.truth,1,0)
data.1$sechand.accuracy_precise <- ifelse(data.1$sechand.perception == data.1$sechand.truth,1,0)
data.1$imp_crime.accuracy_precise <- ifelse(data.1$imp_crime.perception == data.1$imp_crime.truth,1,0)
data.1$imp_discrim.accuracy_precise <- ifelse(data.1$imp_discrim.perception == data.1$imp_discrim.truth,1,0)
data.1$imp_housing.accuracy_precise <- ifelse(data.1$imp_housing.perception == data.1$imp_housing.truth,1,0)
data.1$imp_refugee.accuracy_precise <- ifelse(data.1$imp_refugee.perception == data.1$imp_refugee.truth,1,0)
data.1$imp_climate.accuracy_precise <- ifelse(data.1$imp_climate.perception == data.1$imp_climate.truth,1,0)

```


```{r  fig.width=12, fig.height=8}

#plotting data
df <- rbind(
  data.1[which(data.1$Relationship=="Confidant"), c(81, which(grepl( "accuracy", names(data.1))))],
  data.1[which(data.1$Relationship=="Study partner"), c(81, which(grepl( "accuracy", names(data.1))))],
  data.1[which(data.1$Relationship=="Best Friend"), c(81, which(grepl( "accuracy", names(data.1))))],
  data.1[which(data.1$Relationship=="Sports partner"), c(81, which(grepl( "accuracy", names(data.1))))]
)

# Reshape the data from wide to long format
df_long <- df[,c(1:16)] %>% pivot_longer(-Relationship, names_to = "variable", values_to = "value")

# Convert the variable column to a factor with a specific order
df_long$variable <- factor(df_long$variable, levels = c("LR.accuracy", "imp_crime.accuracy", "imp_climate.accuracy", "imp_discrim.accuracy", "imp_housing.accuracy", "imp_refugee.accuracy", "sechand.accuracy", "replace.accuracy", "animal.accuracy", "fly.accuracy", "meat.accuracy", "nature.accuracy", "cap.accuracy", "student.accuracy", "threat.accuracy"))

#add n and prop. to relationship label, for the plot.
df_long$RelationshipLab <- ifelse(df_long$Relationship=="Confidant", 
                                  paste0("Confidant (n=", length(which(data.1$Relationship=="Confidant")), "; ", round(length(which(data.1$Relationship=="Confidant")) / nrow(data.1) *100,2), "%)"),
                                 ifelse(df_long$Relationship=="Study partner", 
                                        paste0("Study partner (n=", length(which(data.1$Relationship=="Study partner")), "; ", round(length(which(data.1$Relationship=="Study partner")) / nrow(data.1) *100,2), "%)"),
                                                                         ifelse(df_long$Relationship=="Best Friend", 
                                        paste0("Best Friend (n=", length(which(data.1$Relationship=="Best Friend")), "; ", round(length(which(data.1$Relationship=="Best Friend")) / nrow(data.1) *100,2), "%)"),
                                                                         ifelse(df_long$Relationship=="Sports partner", 
                                        paste0("Sports partner (n=", length(which(data.1$Relationship=="Sports partner")), "; ", round(length(which(data.1$Relationship=="Sports partner")) / nrow(data.1) *100,2), "%)"), NA))))
                                        
# create a ggplot object 
p <- ggplot(df_long, aes(x = variable, y = value, fill = variable))

# add a violin plot layer, with each variable represented by a different color
p <- p + geom_violin()

# add summary statistics to the violin plots
p <- p + stat_summary(fun = mean, geom = "point", shape = 18, size = 3, color = "black")
p <- p + stat_summary(fun = median, geom = "point", shape = 23, size = 3, color = "black")
p <- p + stat_summary(geom = "errorbar", fun.data = "median_hilow", color = "black", width = .5)

# facet the plot by group
p <- p + facet_wrap(~ RelationshipLab, nrow = 2)

# add x and y axis labels and a plot title
p <- p + labs(x = "Item", y = "Accuracy score (0-1)", title = paste0("Accuracy scores for alter placement on multiple items, by (monoplex) relationship type (n=", nrow(data.1), ").") , subtitle = "Violin plots showing item-level accuracy distribution with median (transparent square), mean (black square), and IQR (error bars).", caption = "Note: accuracy = abs(perception - truth) / range(item).")

# Adjust the legend position and title
p <- p + theme(legend.position = "right", legend.title = element_blank())

# remove x axis label
p <- p + scale_x_discrete(labels = NULL)

#adjust title text size
p <- p + theme(
  plot.title = element_text(size=16, face="bold"),
  plot.subtitle = element_text(size = 12),
  strip.text = element_text(size = 16),
  legend.text = element_text(size = 12),
  axis.title.y= element_text(size = 16),
  axis.title.x= element_text(size = 16),
  plot.caption = element_text(size = 12),
)

#last, give custom labels for the items
p <- p + scale_fill_discrete(labels = c("Left-right placement (0-10)", "Political importance: crime (1-4)", "Political importance: climate & environment (1-4)", "Political importance: discrimination (1-4)", "Political importance: housing (1-4)", "Political importance: refugee reception (1-4)", "Buying second-hand products (1-4)", "Minimize item replacement (1-4)", "Consuming less animal products (1-4)", "Flight tax (1-4)", "Meat tax (1-4)", "Expanding nature reserves (1-4)", "Annual refugee admissions cap (1-4)", "Foreign students enrich Dutch universities (1-4)", "Migrant arrival threatens Dutch culture (1-4)"  ))

print(p)

```
  


<br>

## different accuracy calculation {.tabset .tabset-fade} 

Accuracy has no clear relationship with relationship type. Let's try different operationalizations of 'accuracy':

1. does the perception and the self-report/truth fall on the same side of the midpoint of the scale? (`accuracy_side`)
2. does the perception precisely match the self-report/truth? (`accuracy_precise`)

### accuracy_side

```{r  fig.width=12, fig.height=8}
#plotting data
df <- rbind(
  data.1[which(data.1$Relationship=="Confidant"), c(81, which(grepl( "accuracy_side", names(data.1))))],
  data.1[which(data.1$Relationship=="Study partner"), c(81, which(grepl( "accuracy_side", names(data.1))))],
  data.1[which(data.1$Relationship=="Best Friend"), c(81, which(grepl( "accuracy_side", names(data.1))))],
  data.1[which(data.1$Relationship=="Sports partner"), c(81, which(grepl( "accuracy_side", names(data.1))))]
)

# Reshape the data from wide to long format
df_long <- df %>% pivot_longer(-Relationship, names_to = "variable", values_to = "value")

# Convert the variable column to a factor with a specific order
df_long$variable <- factor(df_long$variable, levels = c("LR.accuracy_side", "imp_crime.accuracy_side", "imp_climate.accuracy_side", "imp_discrim.accuracy_side", "imp_housing.accuracy_side", "imp_refugee.accuracy_side", "sechand.accuracy_side", "replace.accuracy_side", "animal.accuracy_side", "fly.accuracy_side", "meat.accuracy_side", "nature.accuracy_side", "cap.accuracy_side", "student.accuracy_side", "threat.accuracy_side"))

#add n and prop. to relationship label, for the plot.
df_long$RelationshipLab <- ifelse(df_long$Relationship=="Confidant", 
                                  paste0("Confidant (n=", length(which(data.1$Relationship=="Confidant")), "; ", round(length(which(data.1$Relationship=="Confidant")) / nrow(data.1) *100,2), "%)"),
                                 ifelse(df_long$Relationship=="Study partner", 
                                        paste0("Study partner (n=", length(which(data.1$Relationship=="Study partner")), "; ", round(length(which(data.1$Relationship=="Study partner")) / nrow(data.1) *100,2), "%)"),
                                                                         ifelse(df_long$Relationship=="Best Friend", 
                                        paste0("Best Friend (n=", length(which(data.1$Relationship=="Best Friend")), "; ", round(length(which(data.1$Relationship=="Best Friend")) / nrow(data.1) *100,2), "%)"),
                                                                         ifelse(df_long$Relationship=="Sports partner", 
                                        paste0("Sports partner (n=", length(which(data.1$Relationship=="Sports partner")), "; ", round(length(which(data.1$Relationship=="Sports partner")) / nrow(data.1) *100,2), "%)"), NA))))

# Calculate proportion of 'accurates_sides' for each item and group
prop_df <- aggregate(value ~ variable + RelationshipLab, data = df_long, FUN = mean)

# Create stacked bar chart
p <- ggplot(prop_df, aes(x = variable, y = value, fill = variable))
p <- p + geom_bar(stat = "identity")
p <- p + facet_wrap (~ RelationshipLab, ncol = 2)

# add x and y axis labels and a plot title
p <- p + labs(x = "Item", y = "Proportion accurate_side", title = paste0("Proportion accurate_side placement across multiple items, by (monoplex) relationship type (n=", nrow(data.1), ")."))

# Add horizontal line at 0.5
p <- p + geom_hline(yintercept = 0.5, linetype = "dashed", color = "black")

# Add labels above each bar
p <- p + geom_text(aes(label = round(value, 2)), position = position_stack(vjust = .9))

# Adjust the legend position and title
p <- p + theme(legend.position = "right", legend.title = element_blank())

# remove x axis label
p <- p + scale_x_discrete(labels = NULL)

#adjust title text size
p <- p + theme(
  plot.title = element_text(size=16, face="bold"),
  plot.subtitle = element_text(size = 12),
  strip.text = element_text(size = 16),
  legend.text = element_text(size = 12),
  axis.title.y= element_text(size = 16),
  axis.title.x= element_text(size = 16),
  plot.caption = element_text(size = 12),
)

#last, give custom labels for the items
p <- p + scale_fill_discrete(labels = c("Left-right placement (0-10)", "Political importance: crime (1-4)", "Political importance: climate & environment (1-4)", "Political importance: discrimination (1-4)", "Political importance: housing (1-4)", "Political importance: refugee reception (1-4)", "Buying second-hand products (1-4)", "Minimize item replacement (1-4)", "Consuming less animal products (1-4)", "Flight tax (1-4)", "Meat tax (1-4)", "Expanding nature reserves (1-4)", "Annual refugee admissions cap (1-4)", "Foreign students enrich Dutch universities (1-4)", "Migrant arrival threatens Dutch culture (1-4)"  ))

print(p)

```
  
### accuracy_precise  
  
```{r  fig.width=12, fig.height=8}
#plotting data
df <- rbind(
  data.1[which(data.1$Relationship=="Confidant"), c(81, which(grepl( "accuracy_precise", names(data.1))))],
  data.1[which(data.1$Relationship=="Study partner"), c(81, which(grepl( "accuracy_precise", names(data.1))))],
  data.1[which(data.1$Relationship=="Best Friend"), c(81, which(grepl( "accuracy_precise", names(data.1))))],
  data.1[which(data.1$Relationship=="Sports partner"), c(81, which(grepl( "accuracy_precise", names(data.1))))]
)

# Reshape the data from wide to long format
df_long <- df %>% pivot_longer(-Relationship, names_to = "variable", values_to = "value")

# Convert the variable column to a factor with a specific order
df_long$variable <- factor(df_long$variable, levels = c("LR.accuracy_precise", "imp_crime.accuracy_precise", "imp_climate.accuracy_precise", "imp_discrim.accuracy_precise", "imp_housing.accuracy_precise", "imp_refugee.accuracy_precise", "sechand.accuracy_precise", "replace.accuracy_precise", "animal.accuracy_precise", "fly.accuracy_precise", "meat.accuracy_precise", "nature.accuracy_precise", "cap.accuracy_precise", "student.accuracy_precise", "threat.accuracy_precise"))

#add n and prop. to relationship label, for the plot.
df_long$RelationshipLab <- ifelse(df_long$Relationship=="Confidant", 
                                  paste0("Confidant (n=", length(which(data.1$Relationship=="Confidant")), "; ", round(length(which(data.1$Relationship=="Confidant")) / nrow(data.1) *100,2), "%)"),
                                 ifelse(df_long$Relationship=="Study partner", 
                                        paste0("Study partner (n=", length(which(data.1$Relationship=="Study partner")), "; ", round(length(which(data.1$Relationship=="Study partner")) / nrow(data.1) *100,2), "%)"),
                                                                         ifelse(df_long$Relationship=="Best Friend", 
                                        paste0("Best Friend (n=", length(which(data.1$Relationship=="Best Friend")), "; ", round(length(which(data.1$Relationship=="Best Friend")) / nrow(data.1) *100,2), "%)"),
                                                                         ifelse(df_long$Relationship=="Sports partner", 
                                        paste0("Sports partner (n=", length(which(data.1$Relationship=="Sports partner")), "; ", round(length(which(data.1$Relationship=="Sports partner")) / nrow(data.1) *100,2), "%)"), NA))))

# Calculate proportion of 'accurates_sides' for each item and group
prop_df <- aggregate(value ~ variable + RelationshipLab, data = df_long, FUN = mean)

# Create stacked bar chart
p <- ggplot(prop_df, aes(x = variable, y = value, fill = variable))
p <- p + geom_bar(stat = "identity")
p <- p + facet_wrap (~ RelationshipLab, ncol = 2)

# add x and y axis labels and a plot title
p <- p + labs(x = "Item", y = "Proportion accurate_precise", title = paste0("Proportion accurate_precise placement across multiple items, by (monoplex) relationship type (n=", nrow(data.1), ")."))

# Add horizontal line at 0.5
p <- p + geom_hline(yintercept = 0.5, linetype = "dashed", color = "black")

# Add labels above each bar
p <- p + geom_text(aes(label = round(value, 2)), position = position_stack(vjust = .9))

# Adjust the legend position and title
p <- p + theme(legend.position = "right", legend.title = element_blank())

# remove x axis label
p <- p + scale_x_discrete(labels = NULL)

#adjust title text size
p <- p + theme(
  plot.title = element_text(size=16, face="bold"),
  plot.subtitle = element_text(size = 12),
  strip.text = element_text(size = 16),
  legend.text = element_text(size = 12),
  axis.title.y= element_text(size = 16),
  axis.title.x= element_text(size = 16),
  plot.caption = element_text(size = 12),
)

#last, give custom labels for the items
p <- p + scale_fill_discrete(labels = c("Left-right placement (0-10)", "Political importance: crime (1-4)", "Political importance: climate & environment (1-4)", "Political importance: discrimination (1-4)", "Political importance: housing (1-4)", "Political importance: refugee reception (1-4)", "Buying second-hand products (1-4)", "Minimize item replacement (1-4)", "Consuming less animal products (1-4)", "Flight tax (1-4)", "Meat tax (1-4)", "Expanding nature reserves (1-4)", "Annual refugee admissions cap (1-4)", "Foreign students enrich Dutch universities (1-4)", "Migrant arrival threatens Dutch culture (1-4)"  ))

print(p)

```

## {.unlisted .unnumbered}


# Embeddedness

Relation between embeddedness and accuracy, across (monoplex) relationship types


```{r  fig.width=12, fig.height=8}
#exclude cases with NA on embeddedness (i.e., alter responses)
df <- data.1[which(!is.na(data.1$embeddedness)),]
#nrow(df) #164 ego-alter dyads

#subset accuracy measures, relationship type, embeddedness and respnr
#names(df)
df <- df[,c(1,19,81,which(grepl("accuracy", names(df))))]

# Reshape the data from wide to long format
df_long <- df %>% pivot_longer(-c(Relationship, embeddedness, respnr), names_to = "variable", values_to = "value")

#add n and prop. to relationship label, for the plot.
df_long$RelationshipLab <- ifelse(df_long$Relationship=="Confidant", 
                                  paste0("Confidant (n=", length(which(df$Relationship=="Confidant")), "; ", round(length(which(df$Relationship=="Confidant")) / nrow(df) *100,2), "%)"),
                                 ifelse(df_long$Relationship=="Study partner", 
                                        paste0("Study partner (n=", length(which(df$Relationship=="Study partner")), "; ", round(length(which(df$Relationship=="Study partner")) / nrow(df) *100,2), "%)"),
                                                                         ifelse(df_long$Relationship=="Best Friend", 
                                        paste0("Best Friend (n=", length(which(df$Relationship=="Best Friend")), "; ", round(length(which(df$Relationship=="Best Friend")) / nrow(df) *100,2), "%)"),
                                                                         ifelse(df_long$Relationship=="Sports partner", 
                                        paste0("Sports partner (n=", length(which(df$Relationship=="Sports partner")), "; ", round(length(which(df$Relationship=="Sports partner")) / nrow(df) *100,2), "%)"), NA))))

#plot
p <- ggplot(df_long, aes(x = embeddedness, y = value))
  
#add scatterplot
p <- p + geom_point() +
  geom_smooth(method = "loess")

#add facets by relationship
p <- p + facet_wrap(.~ RelationshipLab)

p <- p + labs(x = "Structural embeddedness (0-1)", y = "Accuracy score (0-1)", title = "Relation between alter's structural embeddedness and ego's positioning accuracy,\nby (monoplex) relationship type (n=164)." , subtitle = "Scatterplot and LOESS curve", caption = "Note: accuracy = abs(perception - truth) / range(item).")

#title
p <- p + theme(
  plot.title = element_text(size=16, face="bold"),
  plot.subtitle = element_text(size = 12),
  strip.text = element_text(size = 16),
  legend.text = element_text(size = 12),
  axis.title.y= element_text(size = 16),
  axis.title.x= element_text(size = 16),
  plot.caption = element_text(size = 12),
)

print(p)
```


## different accuracy calculation {.tabset .tabset-fade} 


### accuracy_side
```{r  fig.width=12, fig.height=8}

#exclude cases with NA on embeddedness (i.e., alter responses)
df <- data.1[which(!is.na(data.1$embeddedness)),]
#nrow(df) #164 ego-alter dyads

#subset accuracy measures, relationship type, embeddedness and respnr
#names(df)
df <- df[,c(1,19,81,which(grepl("accuracy_side", names(df))))]

# Reshape the data from wide to long format
df_long <- df %>% pivot_longer(-c(Relationship, embeddedness, respnr), names_to = "variable", values_to = "value")

#add n and prop. to relationship label, for the plot.
df_long$RelationshipLab <- ifelse(df_long$Relationship=="Confidant", 
                                  paste0("Confidant (n=", length(which(df$Relationship=="Confidant")), "; ", round(length(which(df$Relationship=="Confidant")) / nrow(df) *100,2), "%)"),
                                 ifelse(df_long$Relationship=="Study partner", 
                                        paste0("Study partner (n=", length(which(df$Relationship=="Study partner")), "; ", round(length(which(df$Relationship=="Study partner")) / nrow(df) *100,2), "%)"),
                                                                         ifelse(df_long$Relationship=="Best Friend", 
                                        paste0("Best Friend (n=", length(which(df$Relationship=="Best Friend")), "; ", round(length(which(df$Relationship=="Best Friend")) / nrow(df) *100,2), "%)"),
                                                                         ifelse(df_long$Relationship=="Sports partner", 
                                        paste0("Sports partner (n=", length(which(df$Relationship=="Sports partner")), "; ", round(length(which(df$Relationship=="Sports partner")) / nrow(df) *100,2), "%)"), NA))))

#plot
p <- ggplot(df_long, aes(x = embeddedness, y = value))
  
#add scatterplot and logistic line
p <- p + geom_point() + geom_smooth(method = "glm", se = FALSE, method.args = list(family = "binomial"))
#?geom_smooth

#add facets by relationship
p <- p + facet_wrap(.~ RelationshipLab)

p <- p + labs(x = "Structural embeddedness (0-1)", y = "Accuracy_side (0, 1)", title = "Relation between alter's structural embeddedness and ego's accuracy_side,\nby (monoplex) relationship type (n=164)." , subtitle = "Scatterplot and GLM line")

#title
p <- p + theme(
  plot.title = element_text(size=16, face="bold"),
  plot.subtitle = element_text(size = 12),
  strip.text = element_text(size = 16),
  legend.text = element_text(size = 12),
  axis.title.y= element_text(size = 16),
  axis.title.x= element_text(size = 16),
  plot.caption = element_text(size = 12),
)

print(p)
```

### accuracy_precise
```{r  fig.width=12, fig.height=8}

#exclude cases with NA on embeddedness (i.e., alter responses)
df <- data.1[which(!is.na(data.1$embeddedness)),]
#nrow(df) #164 ego-alter dyads

#subset accuracy measures, relationship type, embeddedness and respnr
#names(df)
df <- df[,c(1,19,81,which(grepl("accuracy_precise", names(df))))]

# Reshape the data from wide to long format
df_long <- df %>% pivot_longer(-c(Relationship, embeddedness, respnr), names_to = "variable", values_to = "value")

#add n and prop. to relationship label, for the plot.
df_long$RelationshipLab <- ifelse(df_long$Relationship=="Confidant", 
                                  paste0("Confidant (n=", length(which(df$Relationship=="Confidant")), "; ", round(length(which(df$Relationship=="Confidant")) / nrow(df) *100,2), "%)"),
                                 ifelse(df_long$Relationship=="Study partner", 
                                        paste0("Study partner (n=", length(which(df$Relationship=="Study partner")), "; ", round(length(which(df$Relationship=="Study partner")) / nrow(df) *100,2), "%)"),
                                                                         ifelse(df_long$Relationship=="Best Friend", 
                                        paste0("Best Friend (n=", length(which(df$Relationship=="Best Friend")), "; ", round(length(which(df$Relationship=="Best Friend")) / nrow(df) *100,2), "%)"),
                                                                         ifelse(df_long$Relationship=="Sports partner", 
                                        paste0("Sports partner (n=", length(which(df$Relationship=="Sports partner")), "; ", round(length(which(df$Relationship=="Sports partner")) / nrow(df) *100,2), "%)"), NA))))

#plot
p <- ggplot(df_long, aes(x = embeddedness, y = value))
  
#add scatterplot and logistic line
p <- p + geom_point() + geom_smooth(method = "glm", se = FALSE, method.args = list(family = "binomial"))
#?geom_smooth

#add facets by relationship
p <- p + facet_wrap(.~ RelationshipLab)

p <- p + labs(x = "Structural embeddedness (0-1)", y = "Accuracy_precise (0, 1)", title = "Relation between alter's structural embeddedness and ego's accuracy_precise,\nby (monoplex) relationship type (n=164)." , subtitle = "Scatterplot and GLM line")

#title
p <- p + theme(
  plot.title = element_text(size=16, face="bold"),
  plot.subtitle = element_text(size = 12),
  strip.text = element_text(size = 16),
  legend.text = element_text(size = 12),
  axis.title.y= element_text(size = 16),
  axis.title.x= element_text(size = 16),
  plot.caption = element_text(size = 12),
)

print(p)
```

## {.unlisted .unnumbered}

----

# Similarity

Does similarity/agreement differ across relationship types?

```{r  fig.width=12, fig.height=8}
#same violin plot, but replace accuracy with (dis)similarity

#similarity = 1- ( |self-report - truth|)/range
data.1$LR.sim <- 1-abs(data.1$LR.self - data.1$LR.truth)/10
data.1$imp_crime.sim <- 1-abs(data.1$imp_crime.self - data.1$imp_crime.truth)/3
data.1$imp_climate.sim <- 1-abs(data.1$imp_climate.self - data.1$imp_climate.truth)/3
data.1$imp_discrim.sim <- 1-abs(data.1$imp_discrim.self - data.1$imp_discrim.truth)/3
data.1$imp_housing.sim <- 1-abs(data.1$imp_housing.self - data.1$imp_housing.truth)/3
data.1$imp_refugee.sim <- 1-abs(data.1$imp_refugee.self - data.1$imp_refugee.truth)/3
data.1$sechand.sim <- 1 - abs(data.1$sechand.self-data.1$sechand.truth)/3
data.1$replace.sim <- 1 - abs(data.1$replace.self-data.1$replace.truth)/3
data.1$animal.sim <- 1 - abs(data.1$animal.self-data.1$animal.truth)/3
data.1$fly.sim <- 1 - abs(data.1$fly.self-data.1$fly.truth)/3
data.1$meat.sim <- 1 - abs(data.1$meat.self-data.1$meat.truth)/3
data.1$nature.sim <- 1 - abs(data.1$nature.self-data.1$nature.truth)/3
data.1$cap.sim <- 1 - abs(data.1$cap.self-data.1$cap.truth)/3
data.1$student.sim <- 1 - abs(data.1$student.self-data.1$student.truth)/3
data.1$threat.sim <- 1 - abs(data.1$threat.self-data.1$threat.truth)/3

#plotting data
df <- rbind(
  data.1[which(data.1$Relationship=="Confidant"), c(81, which(grepl( ".sim", names(data.1))))],
  data.1[which(data.1$Relationship=="Study partner"), c(81, which(grepl( ".sim", names(data.1))))],
  data.1[which(data.1$Relationship=="Best Friend"), c(81, which(grepl( ".sim", names(data.1))))],
  data.1[which(data.1$Relationship=="Sports partner"), c(81, which(grepl( ".sim", names(data.1))))]
)
#fix(df)
# Reshape the data from wide to long format
df_long <- df %>% pivot_longer(-Relationship, names_to = "variable", values_to = "value")

# Convert the variable column to a factor with a specific order
df_long$variable <- factor(df_long$variable, levels = c("LR.sim", "imp_crime.sim", "imp_climate.sim", "imp_discrim.sim", "imp_housing.sim", "imp_refugee.sim", "sechand.sim", "replace.sim", "animal.sim", "fly.sim", "meat.sim", "nature.sim", "cap.sim", "student.sim", "threat.sim"))

#add n and prop. to relationship label, for the plot.
df_long$RelationshipLab <- ifelse(df_long$Relationship=="Confidant", 
                                  paste0("Confidant (n=", length(which(data.1$Relationship=="Confidant")), "; ", round(length(which(data.1$Relationship=="Confidant")) / nrow(data.1) *100,2), "%)"),
                                 ifelse(df_long$Relationship=="Study partner", 
                                        paste0("Study partner (n=", length(which(data.1$Relationship=="Study partner")), "; ", round(length(which(data.1$Relationship=="Study partner")) / nrow(data.1) *100,2), "%)"),
                                                                         ifelse(df_long$Relationship=="Best Friend", 
                                        paste0("Best Friend (n=", length(which(data.1$Relationship=="Best Friend")), "; ", round(length(which(data.1$Relationship=="Best Friend")) / nrow(data.1) *100,2), "%)"),
                                                                         ifelse(df_long$Relationship=="Sports partner", 
                                        paste0("Sports partner (n=", length(which(data.1$Relationship=="Sports partner")), "; ", round(length(which(data.1$Relationship=="Sports partner")) / nrow(data.1) *100,2), "%)"), NA))))
                                        
# create a ggplot object 
p <- ggplot(df_long, aes(x = variable, y = value, fill = variable))

# add a violin plot layer, with each variable represented by a different color
p <- p + geom_violin()

# add summary statistics to the violin plots
p <- p + stat_summary(fun = mean, geom = "point", shape = 18, size = 3, color = "black")
p <- p + stat_summary(fun = median, geom = "point", shape = 23, size = 3, color = "black")
p <- p + stat_summary(geom = "errorbar", fun.data = "median_hilow", color = "black", width = .5)

# facet the plot by group
p <- p + facet_wrap(~ RelationshipLab, nrow = 2)

# add x and y axis labels and a plot title
p <- p + labs(x = "Item", y = "Similarity score (0-1)", title = paste0("Similarity scores for ego and alter on multiple items, by (monoplex) relationship type (n=", nrow(data.1), ").") , subtitle = "Violin plots showing item-level similarity distribution with median (transparent square), mean (black square), and IQR (error bars).", caption = "Note: similarity = abs(self - truth) / range(item).")

# Adjust the legend position and title
p <- p + theme(legend.position = "right", legend.title = element_blank())

# remove x axis label
p <- p + scale_x_discrete(labels = NULL)

#adjust title text size
p <- p + theme(
  plot.title = element_text(size=16, face="bold"),
  plot.subtitle = element_text(size = 12),
  strip.text = element_text(size = 16),
  legend.text = element_text(size = 12),
  axis.title.y= element_text(size = 16),
  axis.title.x= element_text(size = 16),
  plot.caption = element_text(size = 12),
)


#last, give custom labels for the items
p <- p + scale_fill_discrete(labels = c("Left-right placement (0-10)", "Political importance: crime (1-4)", "Political importance: climate & environment (1-4)", "Political importance: discrimination (1-4)", "Political importance: housing (1-4)", "Political importance: refugee reception (1-4)", "Buying second-hand products (1-4)", "Minimize item replacement (1-4)", "Consuming less animal products (1-4)", "Flight tax (1-4)", "Meat tax (1-4)", "Expanding nature reserves (1-4)", "Annual refugee admissions cap (1-4)", "Foreign students enrich Dutch universities (1-4)", "Migrant arrival threatens Dutch culture (1-4)"  ))

print(p)

```


To-do: check with binary outcome (`accuracy_side` and `accuracy_precise`).

<br>

# outcomes {.tabset .tabset-fade} 

```{r, echo=FALSE}
#self-report (dis)agreement / perceptional (dis)agreement; 2x2
matrix <- matrix(NA, 2,2)
rownames(matrix) <- c("Self-report agreement", "Self-report disagreement")
colnames(matrix) <- c("Perceived agreement", "Perceived disagreement")

matrix[1,1] <- "Aware of agreement"
matrix[1,2] <- "False uniqueness"
matrix[2,1] <- "False consensus"
matrix[2,2] <- "Aware of disagreement"

options(knitr.kable.NA='')
knitr::kable(matrix, "html", caption = "Concept matrix") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
```


## All

```{r  fig.width=12, fig.height=8}
#dataframe: outcome counts, per item, nested in groups/themes
dat <- data.frame(group=rep(c("eco-friendly actions", "climate policy", "migration policy" ),each=12),
           item=rep(c("Buying second-hand products", "Minimize item replacement", "Consuming less animal products", "Flight tax", "Meat tax", "Expanding nature reserves", "Annual refugee admissions cap", "Foreign students enrich Dutch universities", "Migrant arrival threatens Dutch culture"),each=4),
           outcome = c("Aware of agreement", "False uniqueness", "False consensus",  "Aware of disagreement"), n=NA)

#counts
{
dat$n[which(dat$item=="Buying second-hand products")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1$sechand.self %in% c(1,2) & data.1$sechand.truth %in% c(1,2) & data.1$sechand.perception %in% c(1,2)) | (data.1$sechand.self %in% c(3,4) & data.1$sechand.truth %in% c(3,4) & data.1$sechand.perception %in% c(3,4)))),ifelse(dat$outcome=="False consensus", length(which((data.1$sechand.self %in% c(1,2) & data.1$sechand.truth %in% c(3,4) & data.1$sechand.perception %in% c(1,2)) | (data.1$sechand.self %in% c(3,4) & data.1$sechand.truth %in% c(1,2) & data.1$sechand.perception %in% c(3,4)))),ifelse(dat$outcome=="False uniqueness", length(which((data.1$sechand.self %in% c(1,2) & data.1$sechand.truth %in% c(1,2) & data.1$sechand.perception %in% c(3,4)) | (data.1$sechand.self %in% c(3,4) & data.1$sechand.truth %in% c(3,4) & data.1$sechand.perception %in% c(1,2)))),ifelse(dat$outcome=="Aware of disagreement", length(which((data.1$sechand.self %in% c(1,2) & data.1$sechand.truth %in% c(3,4) & data.1$sechand.perception %in% c(3,4)) | (data.1$sechand.self %in% c(3,4) & data.1$sechand.truth %in% c(1,2) & data.1$sechand.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Consuming less animal products")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1$animal.self %in% c(1,2) & data.1$animal.truth %in% c(1,2) & data.1$animal.perception %in% c(1,2)) | (data.1$animal.self %in% c(3,4) & data.1$animal.truth %in% c(3,4) & data.1$animal.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1$animal.self %in% c(1,2) & data.1$animal.truth %in% c(3,4) & data.1$animal.perception %in% c(1,2)) | (data.1$animal.self %in% c(3,4) & data.1$animal.truth %in% c(1,2) & data.1$animal.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1$animal.self %in% c(1,2) & data.1$animal.truth %in% c(1,2) & data.1$animal.perception %in% c(3,4)) | (data.1$animal.self %in% c(3,4) & data.1$animal.truth %in% c(3,4) & data.1$animal.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1$animal.self %in% c(1,2) & data.1$animal.truth %in% c(3,4) & data.1$animal.perception %in% c(3,4)) | (data.1$animal.self %in% c(3,4) & data.1$animal.truth %in% c(1,2) & data.1$animal.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Minimize item replacement")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1$replace.self %in% c(1,2) & data.1$replace.truth %in% c(1,2) & data.1$replace.perception %in% c(1,2)) | (data.1$replace.self %in% c(3,4) & data.1$replace.truth %in% c(3,4) & data.1$replace.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1$replace.self %in% c(1,2) & data.1$replace.truth %in% c(3,4) & data.1$replace.perception %in% c(1,2)) | (data.1$replace.self %in% c(3,4) & data.1$replace.truth %in% c(1,2) & data.1$replace.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1$replace.self %in% c(1,2) & data.1$replace.truth %in% c(1,2) & data.1$replace.perception %in% c(3,4)) | (data.1$replace.self %in% c(3,4) & data.1$replace.truth %in% c(3,4) & data.1$replace.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1$replace.self %in% c(1,2) & data.1$replace.truth %in% c(3,4) & data.1$replace.perception %in% c(3,4)) | (data.1$replace.self %in% c(3,4) & data.1$replace.truth %in% c(1,2) & data.1$replace.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Flight tax")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1$fly.self %in% c(1,2) & data.1$fly.truth %in% c(1,2) & data.1$fly.perception %in% c(1,2)) | (data.1$fly.self %in% c(3,4) & data.1$fly.truth %in% c(3,4) & data.1$fly.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1$fly.self %in% c(1,2) & data.1$fly.truth %in% c(3,4) & data.1$fly.perception %in% c(1,2)) | (data.1$fly.self %in% c(3,4) & data.1$fly.truth %in% c(1,2) & data.1$fly.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1$fly.self %in% c(1,2) & data.1$fly.truth %in% c(1,2) & data.1$fly.perception %in% c(3,4)) | (data.1$fly.self %in% c(3,4) & data.1$fly.truth %in% c(3,4) & data.1$fly.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1$fly.self %in% c(1,2) & data.1$fly.truth %in% c(3,4) & data.1$fly.perception %in% c(3,4)) | (data.1$fly.self %in% c(3,4) & data.1$fly.truth %in% c(1,2) & data.1$fly.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Meat tax")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1$meat.self %in% c(1,2) & data.1$meat.truth %in% c(1,2) & data.1$meat.perception %in% c(1,2)) | (data.1$meat.self %in% c(3,4) & data.1$meat.truth %in% c(3,4) & data.1$meat.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1$meat.self %in% c(1,2) & data.1$meat.truth %in% c(3,4) & data.1$meat.perception %in% c(1,2)) | (data.1$meat.self %in% c(3,4) & data.1$meat.truth %in% c(1,2) & data.1$meat.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1$meat.self %in% c(1,2) & data.1$meat.truth %in% c(1,2) & data.1$meat.perception %in% c(3,4)) | (data.1$meat.self %in% c(3,4) & data.1$meat.truth %in% c(3,4) & data.1$meat.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1$meat.self %in% c(1,2) & data.1$meat.truth %in% c(3,4) & data.1$meat.perception %in% c(3,4)) | (data.1$meat.self %in% c(3,4) & data.1$meat.truth %in% c(1,2) & data.1$meat.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Expanding nature reserves")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1$nature.self %in% c(1,2) & data.1$nature.truth %in% c(1,2) & data.1$nature.perception %in% c(1,2)) | (data.1$nature.self %in% c(3,4) & data.1$nature.truth %in% c(3,4) & data.1$nature.perception %in% c(3,4)))),  ifelse(dat$outcome=="False consensus", length(which((data.1$nature.self %in% c(1,2) & data.1$nature.truth %in% c(3,4) & data.1$nature.perception %in% c(1,2)) | (data.1$nature.self %in% c(3,4) & data.1$nature.truth %in% c(1,2) & data.1$nature.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1$nature.self %in% c(1,2) & data.1$nature.truth %in% c(1,2) & data.1$nature.perception %in% c(3,4)) | (data.1$nature.self %in% c(3,4) & data.1$nature.truth %in% c(3,4) & data.1$nature.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1$nature.self %in% c(1,2) & data.1$nature.truth %in% c(3,4) & data.1$nature.perception %in% c(3,4)) | (data.1$nature.self %in% c(3,4) & data.1$nature.truth %in% c(1,2) & data.1$nature.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Annual refugee admissions cap")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1$cap.self %in% c(1,2) & data.1$cap.truth %in% c(1,2) & data.1$cap.perception %in% c(1,2)) | (data.1$cap.self %in% c(3,4) & data.1$cap.truth %in% c(3,4) & data.1$cap.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1$cap.self %in% c(1,2) & data.1$cap.truth %in% c(3,4) & data.1$cap.perception %in% c(1,2)) | (data.1$cap.self %in% c(3,4) & data.1$cap.truth %in% c(1,2) & data.1$cap.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1$cap.self %in% c(1,2) & data.1$cap.truth %in% c(1,2) & data.1$cap.perception %in% c(3,4)) | (data.1$cap.self %in% c(3,4) & data.1$cap.truth %in% c(3,4) & data.1$cap.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1$cap.self %in% c(1,2) & data.1$cap.truth %in% c(3,4) & data.1$cap.perception %in% c(3,4)) | (data.1$cap.self %in% c(3,4) & data.1$cap.truth %in% c(1,2) & data.1$cap.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Foreign students enrich Dutch universities")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1$student.self %in% c(1,2) & data.1$student.truth %in% c(1,2) & data.1$student.perception %in% c(1,2)) | (data.1$student.self %in% c(3,4) & data.1$student.truth %in% c(3,4) & data.1$student.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1$student.self %in% c(1,2) & data.1$student.truth %in% c(3,4) & data.1$student.perception %in% c(1,2)) | (data.1$student.self %in% c(3,4) & data.1$student.truth %in% c(1,2) & data.1$student.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1$student.self %in% c(1,2) & data.1$student.truth %in% c(1,2) & data.1$student.perception %in% c(3,4)) | (data.1$student.self %in% c(3,4) & data.1$student.truth %in% c(3,4) & data.1$student.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1$student.self %in% c(1,2) & data.1$student.truth %in% c(3,4) & data.1$student.perception %in% c(3,4)) | (data.1$student.self %in% c(3,4) & data.1$student.truth %in% c(1,2) & data.1$student.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Migrant arrival threatens Dutch culture")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1$threat.self %in% c(1,2) & data.1$threat.truth %in% c(1,2) & data.1$threat.perception %in% c(1,2)) | (data.1$threat.self %in% c(3,4) & data.1$threat.truth %in% c(3,4) & data.1$threat.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1$threat.self %in% c(1,2) & data.1$threat.truth %in% c(3,4) & data.1$threat.perception %in% c(1,2)) | (data.1$threat.self %in% c(3,4) & data.1$threat.truth %in% c(1,2) & data.1$threat.perception %in% c(3,4)))),ifelse(dat$outcome=="False uniqueness", length(which((data.1$threat.self %in% c(1,2) & data.1$threat.truth %in% c(1,2) & data.1$threat.perception %in% c(3,4)) | (data.1$threat.self %in% c(3,4) & data.1$threat.truth %in% c(3,4) & data.1$threat.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1$threat.self %in% c(1,2) & data.1$threat.truth %in% c(3,4) & data.1$threat.perception %in% c(3,4)) | (data.1$threat.self %in% c(3,4) & data.1$threat.truth %in% c(1,2) & data.1$threat.perception %in% c(1,2)))), NA ))))

}
#fix(dat)
#check
#for (i in unique(dat$item)) {
#  subdat <- dat[which(dat$item==i),]
#  print( sum(subdat$n))
#} ## OKAY

#also add proportion
dat$prop <- dat$n/328

# Define a color blindness friendly palette
cb_palette <- cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73")


#make ggplot object, for items belonging to themes
p1  <- ggplot(data=subset(dat, group=="eco-friendly actions"), 
       aes(x=factor(dat$item[which(dat$group=="eco-friendly actions")]), 
           y=dat$prop[which(dat$group=="eco-friendly actions")], 
           fill = factor(dat$outcome[which(dat$group=="eco-friendly actions")])))+
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = dat$n[which(dat$group=="eco-friendly actions")]),
            position = position_dodge(width = 0.9), vjust = -0.5) +
  theme(axis.text.x = element_text(size = 12)) +
  labs (x="eco-friendly actions", y="prop.") +
  scale_x_discrete(labels = c("Sechand", "Animal", "Replace")) + 
  scale_y_continuous(limits = c(0, .9)) +
  scale_fill_manual(values = cb_palette) + 
  theme(legend.position="none")

p2 <- ggplot(data=subset(dat, group=="climate policy"), 
                  aes(x=factor(dat$item[which(dat$group=="climate policy")]), 
                      y=dat$prop[which(dat$group=="climate policy")], 
                      fill = factor(dat$outcome[which(dat$group=="climate policy")]))) +
    #add bars (counts)
    geom_bar(stat = "identity", position = "dodge") +
    #and percentage
    geom_text(aes(label = dat$n[which(dat$group=="climate policy")]),
              position = position_dodge(width = 0.9), vjust = -0.5) +
    #adjust item labels (size)
    theme(axis.text.x = element_text(size = 12)) +
    #and axis labels (x=group, y=count)
    labs (x="climate policy", y="prop") + 
      scale_y_continuous(limits = c(0, .9)) +
      scale_x_discrete(labels = c("Flight", "Meat", "Nature")) + 
    scale_fill_manual(values = cb_palette) + 
    #remove legend
    theme(legend.position="none")


p3 <- ggplot(data=subset(dat, group=="migration policy"), 
                  aes(x=factor(dat$item[which(dat$group=="migration policy")]), 
                      y=dat$prop[which(dat$group=="migration policy")], 
                      fill = factor(dat$outcome[which(dat$group=="migration policy")]))) +
    #add bars (counts)
    geom_bar(stat = "identity", position = "dodge") +
    #and percentage
    geom_text(aes(label = dat$n[which(dat$group=="migration policy")]),
              position = position_dodge(width = 0.9), vjust = -0.5) +
    #adjust item labels (size)
    theme(axis.text.x = element_text(size = 12)) +
    #and axis labels (x=group, y=count)
    labs (x="migration policy", y="prop.") +
      scale_y_continuous(limits = c(0, .9)) +
      scale_x_discrete(labels = c("Refugee", "Student", "Migrant")) + 
    scale_fill_manual(values = cb_palette) + 
  #remove legend
    theme(legend.position="none")

# make legend only plot with `flegend` custom function
p4 <- ggplot(data=subset(dat, group=="migration policy"), 
                  aes(x=factor(dat$item[which(dat$group=="migration policy")]), 
                      y=dat$n[which(dat$group=="migration policy")], 
                      fill = factor(dat$outcome[which(dat$group=="migration policy")]))) +
    #add bars (counts)
    geom_bar(stat = "identity", position = "dodge") +
    #and percentage
    geom_text(aes(label = paste0(round(dat$prop[which(dat$group=="migration policy")]*100), "%")),
              position = position_dodge(width = 0.9), vjust = -0.5) +
    #adjust item labels (size)
    theme(axis.text.x = element_text(size = 7)) +
      scale_fill_manual(values = cb_palette) + 
    #and axis labels (x=group, y=count)
    labs (x="migration policy", y="prop.", fill = "Outcome among all ties")

legend <- flegend(p4)  

combined_plot <- gridExtra::grid.arrange(p1,p2,p3,legend,
                        nrow = 1)  
  
```

## Confidants

```{r  fig.width=12, fig.height=8}
#dataframe: outcome counts, per item, nested in groups/themes
dat <- data.frame(group=rep(c("eco-friendly actions", "climate policy", "migration policy" ),each=12),
           item=rep(c("Buying second-hand products", "Minimize item replacement", "Consuming less animal products", "Flight tax", "Meat tax", "Expanding nature reserves", "Annual refugee admissions cap", "Foreign students enrich Dutch universities", "Migrant arrival threatens Dutch culture"),each=4),
           outcome = c("Aware of agreement", "False uniqueness", "False consensus",  "Aware of disagreement"), n=NA)


#subset data of friends
data.1.cdn <- data.1[which(data.1$cdn==1),]

#counts
{
dat$n[which(dat$item=="Buying second-hand products")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.cdn$sechand.self %in% c(1,2) & data.1.cdn$sechand.truth %in% c(1,2) & data.1.cdn$sechand.perception %in% c(1,2)) | (data.1.cdn$sechand.self %in% c(3,4) & data.1.cdn$sechand.truth %in% c(3,4) & data.1.cdn$sechand.perception %in% c(3,4)))),ifelse(dat$outcome=="False consensus", length(which((data.1.cdn$sechand.self %in% c(1,2) & data.1.cdn$sechand.truth %in% c(3,4) & data.1.cdn$sechand.perception %in% c(1,2)) | (data.1.cdn$sechand.self %in% c(3,4) & data.1.cdn$sechand.truth %in% c(1,2) & data.1.cdn$sechand.perception %in% c(3,4)))),ifelse(dat$outcome=="False uniqueness", length(which((data.1.cdn$sechand.self %in% c(1,2) & data.1.cdn$sechand.truth %in% c(1,2) & data.1.cdn$sechand.perception %in% c(3,4)) | (data.1.cdn$sechand.self %in% c(3,4) & data.1.cdn$sechand.truth %in% c(3,4) & data.1.cdn$sechand.perception %in% c(1,2)))),ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.cdn$sechand.self %in% c(1,2) & data.1.cdn$sechand.truth %in% c(3,4) & data.1.cdn$sechand.perception %in% c(3,4)) | (data.1.cdn$sechand.self %in% c(3,4) & data.1.cdn$sechand.truth %in% c(1,2) & data.1.cdn$sechand.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Consuming less animal products")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.cdn$animal.self %in% c(1,2) & data.1.cdn$animal.truth %in% c(1,2) & data.1.cdn$animal.perception %in% c(1,2)) | (data.1.cdn$animal.self %in% c(3,4) & data.1.cdn$animal.truth %in% c(3,4) & data.1.cdn$animal.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.cdn$animal.self %in% c(1,2) & data.1.cdn$animal.truth %in% c(3,4) & data.1.cdn$animal.perception %in% c(1,2)) | (data.1.cdn$animal.self %in% c(3,4) & data.1.cdn$animal.truth %in% c(1,2) & data.1.cdn$animal.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.cdn$animal.self %in% c(1,2) & data.1.cdn$animal.truth %in% c(1,2) & data.1.cdn$animal.perception %in% c(3,4)) | (data.1.cdn$animal.self %in% c(3,4) & data.1.cdn$animal.truth %in% c(3,4) & data.1.cdn$animal.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.cdn$animal.self %in% c(1,2) & data.1.cdn$animal.truth %in% c(3,4) & data.1.cdn$animal.perception %in% c(3,4)) | (data.1.cdn$animal.self %in% c(3,4) & data.1.cdn$animal.truth %in% c(1,2) & data.1.cdn$animal.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Minimize item replacement")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.cdn$replace.self %in% c(1,2) & data.1.cdn$replace.truth %in% c(1,2) & data.1.cdn$replace.perception %in% c(1,2)) | (data.1.cdn$replace.self %in% c(3,4) & data.1.cdn$replace.truth %in% c(3,4) & data.1.cdn$replace.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.cdn$replace.self %in% c(1,2) & data.1.cdn$replace.truth %in% c(3,4) & data.1.cdn$replace.perception %in% c(1,2)) | (data.1.cdn$replace.self %in% c(3,4) & data.1.cdn$replace.truth %in% c(1,2) & data.1.cdn$replace.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.cdn$replace.self %in% c(1,2) & data.1.cdn$replace.truth %in% c(1,2) & data.1.cdn$replace.perception %in% c(3,4)) | (data.1.cdn$replace.self %in% c(3,4) & data.1.cdn$replace.truth %in% c(3,4) & data.1.cdn$replace.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.cdn$replace.self %in% c(1,2) & data.1.cdn$replace.truth %in% c(3,4) & data.1.cdn$replace.perception %in% c(3,4)) | (data.1.cdn$replace.self %in% c(3,4) & data.1.cdn$replace.truth %in% c(1,2) & data.1.cdn$replace.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Flight tax")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.cdn$fly.self %in% c(1,2) & data.1.cdn$fly.truth %in% c(1,2) & data.1.cdn$fly.perception %in% c(1,2)) | (data.1.cdn$fly.self %in% c(3,4) & data.1.cdn$fly.truth %in% c(3,4) & data.1.cdn$fly.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.cdn$fly.self %in% c(1,2) & data.1.cdn$fly.truth %in% c(3,4) & data.1.cdn$fly.perception %in% c(1,2)) | (data.1.cdn$fly.self %in% c(3,4) & data.1.cdn$fly.truth %in% c(1,2) & data.1.cdn$fly.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.cdn$fly.self %in% c(1,2) & data.1.cdn$fly.truth %in% c(1,2) & data.1.cdn$fly.perception %in% c(3,4)) | (data.1.cdn$fly.self %in% c(3,4) & data.1.cdn$fly.truth %in% c(3,4) & data.1.cdn$fly.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.cdn$fly.self %in% c(1,2) & data.1.cdn$fly.truth %in% c(3,4) & data.1.cdn$fly.perception %in% c(3,4)) | (data.1.cdn$fly.self %in% c(3,4) & data.1.cdn$fly.truth %in% c(1,2) & data.1.cdn$fly.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Meat tax")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.cdn$meat.self %in% c(1,2) & data.1.cdn$meat.truth %in% c(1,2) & data.1.cdn$meat.perception %in% c(1,2)) | (data.1.cdn$meat.self %in% c(3,4) & data.1.cdn$meat.truth %in% c(3,4) & data.1.cdn$meat.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.cdn$meat.self %in% c(1,2) & data.1.cdn$meat.truth %in% c(3,4) & data.1.cdn$meat.perception %in% c(1,2)) | (data.1.cdn$meat.self %in% c(3,4) & data.1.cdn$meat.truth %in% c(1,2) & data.1.cdn$meat.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.cdn$meat.self %in% c(1,2) & data.1.cdn$meat.truth %in% c(1,2) & data.1.cdn$meat.perception %in% c(3,4)) | (data.1.cdn$meat.self %in% c(3,4) & data.1.cdn$meat.truth %in% c(3,4) & data.1.cdn$meat.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.cdn$meat.self %in% c(1,2) & data.1.cdn$meat.truth %in% c(3,4) & data.1.cdn$meat.perception %in% c(3,4)) | (data.1.cdn$meat.self %in% c(3,4) & data.1.cdn$meat.truth %in% c(1,2) & data.1.cdn$meat.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Expanding nature reserves")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.cdn$nature.self %in% c(1,2) & data.1.cdn$nature.truth %in% c(1,2) & data.1.cdn$nature.perception %in% c(1,2)) | (data.1.cdn$nature.self %in% c(3,4) & data.1.cdn$nature.truth %in% c(3,4) & data.1.cdn$nature.perception %in% c(3,4)))),  ifelse(dat$outcome=="False consensus", length(which((data.1.cdn$nature.self %in% c(1,2) & data.1.cdn$nature.truth %in% c(3,4) & data.1.cdn$nature.perception %in% c(1,2)) | (data.1.cdn$nature.self %in% c(3,4) & data.1.cdn$nature.truth %in% c(1,2) & data.1.cdn$nature.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.cdn$nature.self %in% c(1,2) & data.1.cdn$nature.truth %in% c(1,2) & data.1.cdn$nature.perception %in% c(3,4)) | (data.1.cdn$nature.self %in% c(3,4) & data.1.cdn$nature.truth %in% c(3,4) & data.1.cdn$nature.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.cdn$nature.self %in% c(1,2) & data.1.cdn$nature.truth %in% c(3,4) & data.1.cdn$nature.perception %in% c(3,4)) | (data.1.cdn$nature.self %in% c(3,4) & data.1.cdn$nature.truth %in% c(1,2) & data.1.cdn$nature.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Annual refugee admissions cap")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.cdn$cap.self %in% c(1,2) & data.1.cdn$cap.truth %in% c(1,2) & data.1.cdn$cap.perception %in% c(1,2)) | (data.1.cdn$cap.self %in% c(3,4) & data.1.cdn$cap.truth %in% c(3,4) & data.1.cdn$cap.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.cdn$cap.self %in% c(1,2) & data.1.cdn$cap.truth %in% c(3,4) & data.1.cdn$cap.perception %in% c(1,2)) | (data.1.cdn$cap.self %in% c(3,4) & data.1.cdn$cap.truth %in% c(1,2) & data.1.cdn$cap.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.cdn$cap.self %in% c(1,2) & data.1.cdn$cap.truth %in% c(1,2) & data.1.cdn$cap.perception %in% c(3,4)) | (data.1.cdn$cap.self %in% c(3,4) & data.1.cdn$cap.truth %in% c(3,4) & data.1.cdn$cap.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.cdn$cap.self %in% c(1,2) & data.1.cdn$cap.truth %in% c(3,4) & data.1.cdn$cap.perception %in% c(3,4)) | (data.1.cdn$cap.self %in% c(3,4) & data.1.cdn$cap.truth %in% c(1,2) & data.1.cdn$cap.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Foreign students enrich Dutch universities")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.cdn$student.self %in% c(1,2) & data.1.cdn$student.truth %in% c(1,2) & data.1.cdn$student.perception %in% c(1,2)) | (data.1.cdn$student.self %in% c(3,4) & data.1.cdn$student.truth %in% c(3,4) & data.1.cdn$student.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.cdn$student.self %in% c(1,2) & data.1.cdn$student.truth %in% c(3,4) & data.1.cdn$student.perception %in% c(1,2)) | (data.1.cdn$student.self %in% c(3,4) & data.1.cdn$student.truth %in% c(1,2) & data.1.cdn$student.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.cdn$student.self %in% c(1,2) & data.1.cdn$student.truth %in% c(1,2) & data.1.cdn$student.perception %in% c(3,4)) | (data.1.cdn$student.self %in% c(3,4) & data.1.cdn$student.truth %in% c(3,4) & data.1.cdn$student.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.cdn$student.self %in% c(1,2) & data.1.cdn$student.truth %in% c(3,4) & data.1.cdn$student.perception %in% c(3,4)) | (data.1.cdn$student.self %in% c(3,4) & data.1.cdn$student.truth %in% c(1,2) & data.1.cdn$student.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Migrant arrival threatens Dutch culture")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.cdn$threat.self %in% c(1,2) & data.1.cdn$threat.truth %in% c(1,2) & data.1.cdn$threat.perception %in% c(1,2)) | (data.1.cdn$threat.self %in% c(3,4) & data.1.cdn$threat.truth %in% c(3,4) & data.1.cdn$threat.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.cdn$threat.self %in% c(1,2) & data.1.cdn$threat.truth %in% c(3,4) & data.1.cdn$threat.perception %in% c(1,2)) | (data.1.cdn$threat.self %in% c(3,4) & data.1.cdn$threat.truth %in% c(1,2) & data.1.cdn$threat.perception %in% c(3,4)))),ifelse(dat$outcome=="False uniqueness", length(which((data.1.cdn$threat.self %in% c(1,2) & data.1.cdn$threat.truth %in% c(1,2) & data.1.cdn$threat.perception %in% c(3,4)) | (data.1.cdn$threat.self %in% c(3,4) & data.1.cdn$threat.truth %in% c(3,4) & data.1.cdn$threat.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.cdn$threat.self %in% c(1,2) & data.1.cdn$threat.truth %in% c(3,4) & data.1.cdn$threat.perception %in% c(3,4)) | (data.1.cdn$threat.self %in% c(3,4) & data.1.cdn$threat.truth %in% c(1,2) & data.1.cdn$threat.perception %in% c(1,2)))), NA ))))

}
#fix(dat)
#check
#for (i in unique(dat$item)) {
#  subdat <- dat[which(dat$item==i),]
#  print( sum(subdat$n))
#} ## OKAY

#also add proportion
dat$prop <- dat$n/24

# Define a color blindness friendly palette
cb_palette <- cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73")


#make ggplot object, for items belonging to themes
p1  <- ggplot(data=subset(dat, group=="eco-friendly actions"), 
       aes(x=factor(dat$item[which(dat$group=="eco-friendly actions")]), 
           y=dat$prop[which(dat$group=="eco-friendly actions")], 
           fill = factor(dat$outcome[which(dat$group=="eco-friendly actions")])))+
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = dat$n[which(dat$group=="eco-friendly actions")]),
            position = position_dodge(width = 0.9), vjust = -0.5) +
  theme(axis.text.x = element_text(size = 12)) +
  labs (x="eco-friendly actions", y="prop.") +
  scale_x_discrete(labels = c("Sechand", "Animal", "Replace")) + 
  scale_y_continuous(limits = c(0, .9)) +
  scale_fill_manual(values = cb_palette) + 
  theme(legend.position="none")

p2 <- ggplot(data=subset(dat, group=="climate policy"), 
                  aes(x=factor(dat$item[which(dat$group=="climate policy")]), 
                      y=dat$prop[which(dat$group=="climate policy")], 
                      fill = factor(dat$outcome[which(dat$group=="climate policy")]))) +
    #add bars (counts)
    geom_bar(stat = "identity", position = "dodge") +
    #and percentage
    geom_text(aes(label = dat$n[which(dat$group=="climate policy")]),
              position = position_dodge(width = 0.9), vjust = -0.5) +
    #adjust item labels (size)
    theme(axis.text.x = element_text(size = 12)) +
    #and axis labels (x=group, y=count)
    labs (x="climate policy", y="prop") + 
      scale_y_continuous(limits = c(0, .9)) +
      scale_x_discrete(labels = c("Flight", "Meat", "Nature")) + 
    scale_fill_manual(values = cb_palette) + 
    #remove legend
    theme(legend.position="none")


p3 <- ggplot(data=subset(dat, group=="migration policy"), 
                  aes(x=factor(dat$item[which(dat$group=="migration policy")]), 
                      y=dat$prop[which(dat$group=="migration policy")], 
                      fill = factor(dat$outcome[which(dat$group=="migration policy")]))) +
    #add bars (counts)
    geom_bar(stat = "identity", position = "dodge") +
    #and percentage
    geom_text(aes(label = dat$n[which(dat$group=="migration policy")]),
              position = position_dodge(width = 0.9), vjust = -0.5) +
    #adjust item labels (size)
    theme(axis.text.x = element_text(size = 12)) +
    #and axis labels (x=group, y=count)
    labs (x="migration policy", y="prop.") +
      scale_y_continuous(limits = c(0, .9)) +
      scale_x_discrete(labels = c("Refugee", "Student", "Migrant")) + 
    scale_fill_manual(values = cb_palette) + 
  #remove legend
    theme(legend.position="none")

# make legend only plot with `flegend` custom function
p4 <- ggplot(data=subset(dat, group=="migration policy"), 
                  aes(x=factor(dat$item[which(dat$group=="migration policy")]), 
                      y=dat$n[which(dat$group=="migration policy")], 
                      fill = factor(dat$outcome[which(dat$group=="migration policy")]))) +
    #add bars (counts)
    geom_bar(stat = "identity", position = "dodge") +
    #and percentage
    geom_text(aes(label = paste0(round(dat$prop[which(dat$group=="migration policy")]*100), "%")),
              position = position_dodge(width = 0.9), vjust = -0.5) +
    #adjust item labels (size)
    theme(axis.text.x = element_text(size = 7)) +
      scale_fill_manual(values = cb_palette) + 
    #and axis labels (x=group, y=count)
    labs (x="migration policy", y="prop.", fill = "Outcome in confiding ties")

legend <- flegend(p4)  

combined_plot <- gridExtra::grid.arrange(p1,p2,p3,legend,
                        nrow = 1)  
 
```

## Study

```{r  fig.width=12, fig.height=8}
#dataframe: outcome counts, per item, nested in groups/themes
dat <- data.frame(group=rep(c("eco-friendly actions", "climate policy", "migration policy" ),each=12),
           item=rep(c("Buying second-hand products", "Minimize item replacement", "Consuming less animal products", "Flight tax", "Meat tax", "Expanding nature reserves", "Annual refugee admissions cap", "Foreign students enrich Dutch universities", "Migrant arrival threatens Dutch culture"),each=4),
           outcome = c("Aware of agreement", "False uniqueness", "False consensus",  "Aware of disagreement"), n=NA)


#subset data of friends
data.1.study <- data.1[which(data.1$study==1),]

#counts
{
dat$n[which(dat$item=="Buying second-hand products")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.study$sechand.self %in% c(1,2) & data.1.study$sechand.truth %in% c(1,2) & data.1.study$sechand.perception %in% c(1,2)) | (data.1.study$sechand.self %in% c(3,4) & data.1.study$sechand.truth %in% c(3,4) & data.1.study$sechand.perception %in% c(3,4)))),ifelse(dat$outcome=="False consensus", length(which((data.1.study$sechand.self %in% c(1,2) & data.1.study$sechand.truth %in% c(3,4) & data.1.study$sechand.perception %in% c(1,2)) | (data.1.study$sechand.self %in% c(3,4) & data.1.study$sechand.truth %in% c(1,2) & data.1.study$sechand.perception %in% c(3,4)))),ifelse(dat$outcome=="False uniqueness", length(which((data.1.study$sechand.self %in% c(1,2) & data.1.study$sechand.truth %in% c(1,2) & data.1.study$sechand.perception %in% c(3,4)) | (data.1.study$sechand.self %in% c(3,4) & data.1.study$sechand.truth %in% c(3,4) & data.1.study$sechand.perception %in% c(1,2)))),ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.study$sechand.self %in% c(1,2) & data.1.study$sechand.truth %in% c(3,4) & data.1.study$sechand.perception %in% c(3,4)) | (data.1.study$sechand.self %in% c(3,4) & data.1.study$sechand.truth %in% c(1,2) & data.1.study$sechand.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Consuming less animal products")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.study$animal.self %in% c(1,2) & data.1.study$animal.truth %in% c(1,2) & data.1.study$animal.perception %in% c(1,2)) | (data.1.study$animal.self %in% c(3,4) & data.1.study$animal.truth %in% c(3,4) & data.1.study$animal.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.study$animal.self %in% c(1,2) & data.1.study$animal.truth %in% c(3,4) & data.1.study$animal.perception %in% c(1,2)) | (data.1.study$animal.self %in% c(3,4) & data.1.study$animal.truth %in% c(1,2) & data.1.study$animal.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.study$animal.self %in% c(1,2) & data.1.study$animal.truth %in% c(1,2) & data.1.study$animal.perception %in% c(3,4)) | (data.1.study$animal.self %in% c(3,4) & data.1.study$animal.truth %in% c(3,4) & data.1.study$animal.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.study$animal.self %in% c(1,2) & data.1.study$animal.truth %in% c(3,4) & data.1.study$animal.perception %in% c(3,4)) | (data.1.study$animal.self %in% c(3,4) & data.1.study$animal.truth %in% c(1,2) & data.1.study$animal.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Minimize item replacement")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.study$replace.self %in% c(1,2) & data.1.study$replace.truth %in% c(1,2) & data.1.study$replace.perception %in% c(1,2)) | (data.1.study$replace.self %in% c(3,4) & data.1.study$replace.truth %in% c(3,4) & data.1.study$replace.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.study$replace.self %in% c(1,2) & data.1.study$replace.truth %in% c(3,4) & data.1.study$replace.perception %in% c(1,2)) | (data.1.study$replace.self %in% c(3,4) & data.1.study$replace.truth %in% c(1,2) & data.1.study$replace.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.study$replace.self %in% c(1,2) & data.1.study$replace.truth %in% c(1,2) & data.1.study$replace.perception %in% c(3,4)) | (data.1.study$replace.self %in% c(3,4) & data.1.study$replace.truth %in% c(3,4) & data.1.study$replace.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.study$replace.self %in% c(1,2) & data.1.study$replace.truth %in% c(3,4) & data.1.study$replace.perception %in% c(3,4)) | (data.1.study$replace.self %in% c(3,4) & data.1.study$replace.truth %in% c(1,2) & data.1.study$replace.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Flight tax")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.study$fly.self %in% c(1,2) & data.1.study$fly.truth %in% c(1,2) & data.1.study$fly.perception %in% c(1,2)) | (data.1.study$fly.self %in% c(3,4) & data.1.study$fly.truth %in% c(3,4) & data.1.study$fly.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.study$fly.self %in% c(1,2) & data.1.study$fly.truth %in% c(3,4) & data.1.study$fly.perception %in% c(1,2)) | (data.1.study$fly.self %in% c(3,4) & data.1.study$fly.truth %in% c(1,2) & data.1.study$fly.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.study$fly.self %in% c(1,2) & data.1.study$fly.truth %in% c(1,2) & data.1.study$fly.perception %in% c(3,4)) | (data.1.study$fly.self %in% c(3,4) & data.1.study$fly.truth %in% c(3,4) & data.1.study$fly.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.study$fly.self %in% c(1,2) & data.1.study$fly.truth %in% c(3,4) & data.1.study$fly.perception %in% c(3,4)) | (data.1.study$fly.self %in% c(3,4) & data.1.study$fly.truth %in% c(1,2) & data.1.study$fly.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Meat tax")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.study$meat.self %in% c(1,2) & data.1.study$meat.truth %in% c(1,2) & data.1.study$meat.perception %in% c(1,2)) | (data.1.study$meat.self %in% c(3,4) & data.1.study$meat.truth %in% c(3,4) & data.1.study$meat.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.study$meat.self %in% c(1,2) & data.1.study$meat.truth %in% c(3,4) & data.1.study$meat.perception %in% c(1,2)) | (data.1.study$meat.self %in% c(3,4) & data.1.study$meat.truth %in% c(1,2) & data.1.study$meat.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.study$meat.self %in% c(1,2) & data.1.study$meat.truth %in% c(1,2) & data.1.study$meat.perception %in% c(3,4)) | (data.1.study$meat.self %in% c(3,4) & data.1.study$meat.truth %in% c(3,4) & data.1.study$meat.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.study$meat.self %in% c(1,2) & data.1.study$meat.truth %in% c(3,4) & data.1.study$meat.perception %in% c(3,4)) | (data.1.study$meat.self %in% c(3,4) & data.1.study$meat.truth %in% c(1,2) & data.1.study$meat.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Expanding nature reserves")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.study$nature.self %in% c(1,2) & data.1.study$nature.truth %in% c(1,2) & data.1.study$nature.perception %in% c(1,2)) | (data.1.study$nature.self %in% c(3,4) & data.1.study$nature.truth %in% c(3,4) & data.1.study$nature.perception %in% c(3,4)))),  ifelse(dat$outcome=="False consensus", length(which((data.1.study$nature.self %in% c(1,2) & data.1.study$nature.truth %in% c(3,4) & data.1.study$nature.perception %in% c(1,2)) | (data.1.study$nature.self %in% c(3,4) & data.1.study$nature.truth %in% c(1,2) & data.1.study$nature.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.study$nature.self %in% c(1,2) & data.1.study$nature.truth %in% c(1,2) & data.1.study$nature.perception %in% c(3,4)) | (data.1.study$nature.self %in% c(3,4) & data.1.study$nature.truth %in% c(3,4) & data.1.study$nature.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.study$nature.self %in% c(1,2) & data.1.study$nature.truth %in% c(3,4) & data.1.study$nature.perception %in% c(3,4)) | (data.1.study$nature.self %in% c(3,4) & data.1.study$nature.truth %in% c(1,2) & data.1.study$nature.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Annual refugee admissions cap")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.study$cap.self %in% c(1,2) & data.1.study$cap.truth %in% c(1,2) & data.1.study$cap.perception %in% c(1,2)) | (data.1.study$cap.self %in% c(3,4) & data.1.study$cap.truth %in% c(3,4) & data.1.study$cap.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.study$cap.self %in% c(1,2) & data.1.study$cap.truth %in% c(3,4) & data.1.study$cap.perception %in% c(1,2)) | (data.1.study$cap.self %in% c(3,4) & data.1.study$cap.truth %in% c(1,2) & data.1.study$cap.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.study$cap.self %in% c(1,2) & data.1.study$cap.truth %in% c(1,2) & data.1.study$cap.perception %in% c(3,4)) | (data.1.study$cap.self %in% c(3,4) & data.1.study$cap.truth %in% c(3,4) & data.1.study$cap.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.study$cap.self %in% c(1,2) & data.1.study$cap.truth %in% c(3,4) & data.1.study$cap.perception %in% c(3,4)) | (data.1.study$cap.self %in% c(3,4) & data.1.study$cap.truth %in% c(1,2) & data.1.study$cap.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Foreign students enrich Dutch universities")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.study$student.self %in% c(1,2) & data.1.study$student.truth %in% c(1,2) & data.1.study$student.perception %in% c(1,2)) | (data.1.study$student.self %in% c(3,4) & data.1.study$student.truth %in% c(3,4) & data.1.study$student.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.study$student.self %in% c(1,2) & data.1.study$student.truth %in% c(3,4) & data.1.study$student.perception %in% c(1,2)) | (data.1.study$student.self %in% c(3,4) & data.1.study$student.truth %in% c(1,2) & data.1.study$student.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.study$student.self %in% c(1,2) & data.1.study$student.truth %in% c(1,2) & data.1.study$student.perception %in% c(3,4)) | (data.1.study$student.self %in% c(3,4) & data.1.study$student.truth %in% c(3,4) & data.1.study$student.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.study$student.self %in% c(1,2) & data.1.study$student.truth %in% c(3,4) & data.1.study$student.perception %in% c(3,4)) | (data.1.study$student.self %in% c(3,4) & data.1.study$student.truth %in% c(1,2) & data.1.study$student.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Migrant arrival threatens Dutch culture")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.study$threat.self %in% c(1,2) & data.1.study$threat.truth %in% c(1,2) & data.1.study$threat.perception %in% c(1,2)) | (data.1.study$threat.self %in% c(3,4) & data.1.study$threat.truth %in% c(3,4) & data.1.study$threat.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.study$threat.self %in% c(1,2) & data.1.study$threat.truth %in% c(3,4) & data.1.study$threat.perception %in% c(1,2)) | (data.1.study$threat.self %in% c(3,4) & data.1.study$threat.truth %in% c(1,2) & data.1.study$threat.perception %in% c(3,4)))),ifelse(dat$outcome=="False uniqueness", length(which((data.1.study$threat.self %in% c(1,2) & data.1.study$threat.truth %in% c(1,2) & data.1.study$threat.perception %in% c(3,4)) | (data.1.study$threat.self %in% c(3,4) & data.1.study$threat.truth %in% c(3,4) & data.1.study$threat.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.study$threat.self %in% c(1,2) & data.1.study$threat.truth %in% c(3,4) & data.1.study$threat.perception %in% c(3,4)) | (data.1.study$threat.self %in% c(3,4) & data.1.study$threat.truth %in% c(1,2) & data.1.study$threat.perception %in% c(1,2)))), NA ))))

}
#fix(dat)
#check
#for (i in unique(dat$item)) {
#  subdat <- dat[which(dat$item==i),]
#  print( sum(subdat$n))
#} ## OKAY

#also add proportion
dat$prop <- dat$n/54

# Define a color blindness friendly palette
cb_palette <- cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73")


#make ggplot object, for items belonging to themes
p1  <- ggplot(data=subset(dat, group=="eco-friendly actions"), 
       aes(x=factor(dat$item[which(dat$group=="eco-friendly actions")]), 
           y=dat$prop[which(dat$group=="eco-friendly actions")], 
           fill = factor(dat$outcome[which(dat$group=="eco-friendly actions")])))+
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = dat$n[which(dat$group=="eco-friendly actions")]),
            position = position_dodge(width = 0.9), vjust = -0.5) +
  theme(axis.text.x = element_text(size = 12)) +
  labs (x="eco-friendly actions", y="prop.") +
  scale_x_discrete(labels = c("Sechand", "Animal", "Replace")) + 
  scale_y_continuous(limits = c(0, .9)) +
  scale_fill_manual(values = cb_palette) + 
  theme(legend.position="none")

p2 <- ggplot(data=subset(dat, group=="climate policy"), 
                  aes(x=factor(dat$item[which(dat$group=="climate policy")]), 
                      y=dat$prop[which(dat$group=="climate policy")], 
                      fill = factor(dat$outcome[which(dat$group=="climate policy")]))) +
    #add bars (counts)
    geom_bar(stat = "identity", position = "dodge") +
    #and percentage
    geom_text(aes(label = dat$n[which(dat$group=="climate policy")]),
              position = position_dodge(width = 0.9), vjust = -0.5) +
    #adjust item labels (size)
    theme(axis.text.x = element_text(size = 12)) +
    #and axis labels (x=group, y=count)
    labs (x="climate policy", y="prop") + 
      scale_y_continuous(limits = c(0, .9)) +
      scale_x_discrete(labels = c("Flight", "Meat", "Nature")) + 
    scale_fill_manual(values = cb_palette) + 
    #remove legend
    theme(legend.position="none")


p3 <- ggplot(data=subset(dat, group=="migration policy"), 
                  aes(x=factor(dat$item[which(dat$group=="migration policy")]), 
                      y=dat$prop[which(dat$group=="migration policy")], 
                      fill = factor(dat$outcome[which(dat$group=="migration policy")]))) +
    #add bars (counts)
    geom_bar(stat = "identity", position = "dodge") +
    #and percentage
    geom_text(aes(label = dat$n[which(dat$group=="migration policy")]),
              position = position_dodge(width = 0.9), vjust = -0.5) +
    #adjust item labels (size)
    theme(axis.text.x = element_text(size = 12)) +
    #and axis labels (x=group, y=count)
    labs (x="migration policy", y="prop.") +
      scale_y_continuous(limits = c(0, .9)) +
      scale_x_discrete(labels = c("Refugee", "Student", "Migrant")) + 
    scale_fill_manual(values = cb_palette) + 
  #remove legend
    theme(legend.position="none")

# make legend only plot with `flegend` custom function
p4 <- ggplot(data=subset(dat, group=="migration policy"), 
                  aes(x=factor(dat$item[which(dat$group=="migration policy")]), 
                      y=dat$n[which(dat$group=="migration policy")], 
                      fill = factor(dat$outcome[which(dat$group=="migration policy")]))) +
    #add bars (counts)
    geom_bar(stat = "identity", position = "dodge") +
    #and percentage
    geom_text(aes(label = paste0(round(dat$prop[which(dat$group=="migration policy")]*100), "%")),
              position = position_dodge(width = 0.9), vjust = -0.5) +
    #adjust item labels (size)
    theme(axis.text.x = element_text(size = 7)) +
      scale_fill_manual(values = cb_palette) + 
    #and axis labels (x=group, y=count)
    labs (x="migration policy", y="prop.", fill = "Outcome in studying ties")

legend <- flegend(p4)  

combined_plot <- gridExtra::grid.arrange(p1,p2,p3,legend,
                        nrow = 1)  
 
```


## Friends

```{r  fig.width=12, fig.height=8}
#dataframe: outcome counts, per item, nested in groups/themes
dat <- data.frame(group=rep(c("eco-friendly actions", "climate policy", "migration policy" ),each=12),
           item=rep(c("Buying second-hand products", "Minimize item replacement", "Consuming less animal products", "Flight tax", "Meat tax", "Expanding nature reserves", "Annual refugee admissions cap", "Foreign students enrich Dutch universities", "Migrant arrival threatens Dutch culture"),each=4),
           outcome = c("Aware of agreement", "False uniqueness", "False consensus",  "Aware of disagreement"), n=NA)


#subset data of friends
data.1.bff <- data.1[which(data.1$bff==1),]

#counts
{
dat$n[which(dat$item=="Buying second-hand products")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.bff$sechand.self %in% c(1,2) & data.1.bff$sechand.truth %in% c(1,2) & data.1.bff$sechand.perception %in% c(1,2)) | (data.1.bff$sechand.self %in% c(3,4) & data.1.bff$sechand.truth %in% c(3,4) & data.1.bff$sechand.perception %in% c(3,4)))),ifelse(dat$outcome=="False consensus", length(which((data.1.bff$sechand.self %in% c(1,2) & data.1.bff$sechand.truth %in% c(3,4) & data.1.bff$sechand.perception %in% c(1,2)) | (data.1.bff$sechand.self %in% c(3,4) & data.1.bff$sechand.truth %in% c(1,2) & data.1.bff$sechand.perception %in% c(3,4)))),ifelse(dat$outcome=="False uniqueness", length(which((data.1.bff$sechand.self %in% c(1,2) & data.1.bff$sechand.truth %in% c(1,2) & data.1.bff$sechand.perception %in% c(3,4)) | (data.1.bff$sechand.self %in% c(3,4) & data.1.bff$sechand.truth %in% c(3,4) & data.1.bff$sechand.perception %in% c(1,2)))),ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.bff$sechand.self %in% c(1,2) & data.1.bff$sechand.truth %in% c(3,4) & data.1.bff$sechand.perception %in% c(3,4)) | (data.1.bff$sechand.self %in% c(3,4) & data.1.bff$sechand.truth %in% c(1,2) & data.1.bff$sechand.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Consuming less animal products")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.bff$animal.self %in% c(1,2) & data.1.bff$animal.truth %in% c(1,2) & data.1.bff$animal.perception %in% c(1,2)) | (data.1.bff$animal.self %in% c(3,4) & data.1.bff$animal.truth %in% c(3,4) & data.1.bff$animal.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.bff$animal.self %in% c(1,2) & data.1.bff$animal.truth %in% c(3,4) & data.1.bff$animal.perception %in% c(1,2)) | (data.1.bff$animal.self %in% c(3,4) & data.1.bff$animal.truth %in% c(1,2) & data.1.bff$animal.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.bff$animal.self %in% c(1,2) & data.1.bff$animal.truth %in% c(1,2) & data.1.bff$animal.perception %in% c(3,4)) | (data.1.bff$animal.self %in% c(3,4) & data.1.bff$animal.truth %in% c(3,4) & data.1.bff$animal.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.bff$animal.self %in% c(1,2) & data.1.bff$animal.truth %in% c(3,4) & data.1.bff$animal.perception %in% c(3,4)) | (data.1.bff$animal.self %in% c(3,4) & data.1.bff$animal.truth %in% c(1,2) & data.1.bff$animal.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Minimize item replacement")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.bff$replace.self %in% c(1,2) & data.1.bff$replace.truth %in% c(1,2) & data.1.bff$replace.perception %in% c(1,2)) | (data.1.bff$replace.self %in% c(3,4) & data.1.bff$replace.truth %in% c(3,4) & data.1.bff$replace.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.bff$replace.self %in% c(1,2) & data.1.bff$replace.truth %in% c(3,4) & data.1.bff$replace.perception %in% c(1,2)) | (data.1.bff$replace.self %in% c(3,4) & data.1.bff$replace.truth %in% c(1,2) & data.1.bff$replace.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.bff$replace.self %in% c(1,2) & data.1.bff$replace.truth %in% c(1,2) & data.1.bff$replace.perception %in% c(3,4)) | (data.1.bff$replace.self %in% c(3,4) & data.1.bff$replace.truth %in% c(3,4) & data.1.bff$replace.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.bff$replace.self %in% c(1,2) & data.1.bff$replace.truth %in% c(3,4) & data.1.bff$replace.perception %in% c(3,4)) | (data.1.bff$replace.self %in% c(3,4) & data.1.bff$replace.truth %in% c(1,2) & data.1.bff$replace.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Flight tax")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.bff$fly.self %in% c(1,2) & data.1.bff$fly.truth %in% c(1,2) & data.1.bff$fly.perception %in% c(1,2)) | (data.1.bff$fly.self %in% c(3,4) & data.1.bff$fly.truth %in% c(3,4) & data.1.bff$fly.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.bff$fly.self %in% c(1,2) & data.1.bff$fly.truth %in% c(3,4) & data.1.bff$fly.perception %in% c(1,2)) | (data.1.bff$fly.self %in% c(3,4) & data.1.bff$fly.truth %in% c(1,2) & data.1.bff$fly.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.bff$fly.self %in% c(1,2) & data.1.bff$fly.truth %in% c(1,2) & data.1.bff$fly.perception %in% c(3,4)) | (data.1.bff$fly.self %in% c(3,4) & data.1.bff$fly.truth %in% c(3,4) & data.1.bff$fly.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.bff$fly.self %in% c(1,2) & data.1.bff$fly.truth %in% c(3,4) & data.1.bff$fly.perception %in% c(3,4)) | (data.1.bff$fly.self %in% c(3,4) & data.1.bff$fly.truth %in% c(1,2) & data.1.bff$fly.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Meat tax")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.bff$meat.self %in% c(1,2) & data.1.bff$meat.truth %in% c(1,2) & data.1.bff$meat.perception %in% c(1,2)) | (data.1.bff$meat.self %in% c(3,4) & data.1.bff$meat.truth %in% c(3,4) & data.1.bff$meat.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.bff$meat.self %in% c(1,2) & data.1.bff$meat.truth %in% c(3,4) & data.1.bff$meat.perception %in% c(1,2)) | (data.1.bff$meat.self %in% c(3,4) & data.1.bff$meat.truth %in% c(1,2) & data.1.bff$meat.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.bff$meat.self %in% c(1,2) & data.1.bff$meat.truth %in% c(1,2) & data.1.bff$meat.perception %in% c(3,4)) | (data.1.bff$meat.self %in% c(3,4) & data.1.bff$meat.truth %in% c(3,4) & data.1.bff$meat.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.bff$meat.self %in% c(1,2) & data.1.bff$meat.truth %in% c(3,4) & data.1.bff$meat.perception %in% c(3,4)) | (data.1.bff$meat.self %in% c(3,4) & data.1.bff$meat.truth %in% c(1,2) & data.1.bff$meat.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Expanding nature reserves")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.bff$nature.self %in% c(1,2) & data.1.bff$nature.truth %in% c(1,2) & data.1.bff$nature.perception %in% c(1,2)) | (data.1.bff$nature.self %in% c(3,4) & data.1.bff$nature.truth %in% c(3,4) & data.1.bff$nature.perception %in% c(3,4)))),  ifelse(dat$outcome=="False consensus", length(which((data.1.bff$nature.self %in% c(1,2) & data.1.bff$nature.truth %in% c(3,4) & data.1.bff$nature.perception %in% c(1,2)) | (data.1.bff$nature.self %in% c(3,4) & data.1.bff$nature.truth %in% c(1,2) & data.1.bff$nature.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.bff$nature.self %in% c(1,2) & data.1.bff$nature.truth %in% c(1,2) & data.1.bff$nature.perception %in% c(3,4)) | (data.1.bff$nature.self %in% c(3,4) & data.1.bff$nature.truth %in% c(3,4) & data.1.bff$nature.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.bff$nature.self %in% c(1,2) & data.1.bff$nature.truth %in% c(3,4) & data.1.bff$nature.perception %in% c(3,4)) | (data.1.bff$nature.self %in% c(3,4) & data.1.bff$nature.truth %in% c(1,2) & data.1.bff$nature.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Annual refugee admissions cap")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.bff$cap.self %in% c(1,2) & data.1.bff$cap.truth %in% c(1,2) & data.1.bff$cap.perception %in% c(1,2)) | (data.1.bff$cap.self %in% c(3,4) & data.1.bff$cap.truth %in% c(3,4) & data.1.bff$cap.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.bff$cap.self %in% c(1,2) & data.1.bff$cap.truth %in% c(3,4) & data.1.bff$cap.perception %in% c(1,2)) | (data.1.bff$cap.self %in% c(3,4) & data.1.bff$cap.truth %in% c(1,2) & data.1.bff$cap.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.bff$cap.self %in% c(1,2) & data.1.bff$cap.truth %in% c(1,2) & data.1.bff$cap.perception %in% c(3,4)) | (data.1.bff$cap.self %in% c(3,4) & data.1.bff$cap.truth %in% c(3,4) & data.1.bff$cap.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.bff$cap.self %in% c(1,2) & data.1.bff$cap.truth %in% c(3,4) & data.1.bff$cap.perception %in% c(3,4)) | (data.1.bff$cap.self %in% c(3,4) & data.1.bff$cap.truth %in% c(1,2) & data.1.bff$cap.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Foreign students enrich Dutch universities")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.bff$student.self %in% c(1,2) & data.1.bff$student.truth %in% c(1,2) & data.1.bff$student.perception %in% c(1,2)) | (data.1.bff$student.self %in% c(3,4) & data.1.bff$student.truth %in% c(3,4) & data.1.bff$student.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.bff$student.self %in% c(1,2) & data.1.bff$student.truth %in% c(3,4) & data.1.bff$student.perception %in% c(1,2)) | (data.1.bff$student.self %in% c(3,4) & data.1.bff$student.truth %in% c(1,2) & data.1.bff$student.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.bff$student.self %in% c(1,2) & data.1.bff$student.truth %in% c(1,2) & data.1.bff$student.perception %in% c(3,4)) | (data.1.bff$student.self %in% c(3,4) & data.1.bff$student.truth %in% c(3,4) & data.1.bff$student.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.bff$student.self %in% c(1,2) & data.1.bff$student.truth %in% c(3,4) & data.1.bff$student.perception %in% c(3,4)) | (data.1.bff$student.self %in% c(3,4) & data.1.bff$student.truth %in% c(1,2) & data.1.bff$student.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Migrant arrival threatens Dutch culture")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.bff$threat.self %in% c(1,2) & data.1.bff$threat.truth %in% c(1,2) & data.1.bff$threat.perception %in% c(1,2)) | (data.1.bff$threat.self %in% c(3,4) & data.1.bff$threat.truth %in% c(3,4) & data.1.bff$threat.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.bff$threat.self %in% c(1,2) & data.1.bff$threat.truth %in% c(3,4) & data.1.bff$threat.perception %in% c(1,2)) | (data.1.bff$threat.self %in% c(3,4) & data.1.bff$threat.truth %in% c(1,2) & data.1.bff$threat.perception %in% c(3,4)))),ifelse(dat$outcome=="False uniqueness", length(which((data.1.bff$threat.self %in% c(1,2) & data.1.bff$threat.truth %in% c(1,2) & data.1.bff$threat.perception %in% c(3,4)) | (data.1.bff$threat.self %in% c(3,4) & data.1.bff$threat.truth %in% c(3,4) & data.1.bff$threat.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.bff$threat.self %in% c(1,2) & data.1.bff$threat.truth %in% c(3,4) & data.1.bff$threat.perception %in% c(3,4)) | (data.1.bff$threat.self %in% c(3,4) & data.1.bff$threat.truth %in% c(1,2) & data.1.bff$threat.perception %in% c(1,2)))), NA ))))

}
#fix(dat)
#check
#for (i in unique(dat$item)) {
#  subdat <- dat[which(dat$item==i),]
#  print( sum(subdat$n))
#} ## OKAY

#also add proportion
dat$prop <- dat$n/152

# Define a color blindness friendly palette
cb_palette <- cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73")


#make ggplot object, for items belonging to themes
p1  <- ggplot(data=subset(dat, group=="eco-friendly actions"), 
       aes(x=factor(dat$item[which(dat$group=="eco-friendly actions")]), 
           y=dat$prop[which(dat$group=="eco-friendly actions")], 
           fill = factor(dat$outcome[which(dat$group=="eco-friendly actions")])))+
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = dat$n[which(dat$group=="eco-friendly actions")]),
            position = position_dodge(width = 0.9), vjust = -0.5) +
  theme(axis.text.x = element_text(size = 12)) +
  labs (x="eco-friendly actions", y="prop.") +
  scale_x_discrete(labels = c("Sechand", "Animal", "Replace")) + 
  scale_y_continuous(limits = c(0, .9)) +
  scale_fill_manual(values = cb_palette) + 
  theme(legend.position="none")

p2 <- ggplot(data=subset(dat, group=="climate policy"), 
                  aes(x=factor(dat$item[which(dat$group=="climate policy")]), 
                      y=dat$prop[which(dat$group=="climate policy")], 
                      fill = factor(dat$outcome[which(dat$group=="climate policy")]))) +
    #add bars (counts)
    geom_bar(stat = "identity", position = "dodge") +
    #and percentage
    geom_text(aes(label = dat$n[which(dat$group=="climate policy")]),
              position = position_dodge(width = 0.9), vjust = -0.5) +
    #adjust item labels (size)
    theme(axis.text.x = element_text(size = 12)) +
    #and axis labels (x=group, y=count)
    labs (x="climate policy", y="prop") + 
      scale_y_continuous(limits = c(0, .9)) +
      scale_x_discrete(labels = c("Flight", "Meat", "Nature")) + 
    scale_fill_manual(values = cb_palette) + 
    #remove legend
    theme(legend.position="none")


p3 <- ggplot(data=subset(dat, group=="migration policy"), 
                  aes(x=factor(dat$item[which(dat$group=="migration policy")]), 
                      y=dat$prop[which(dat$group=="migration policy")], 
                      fill = factor(dat$outcome[which(dat$group=="migration policy")]))) +
    #add bars (counts)
    geom_bar(stat = "identity", position = "dodge") +
    #and percentage
    geom_text(aes(label = dat$n[which(dat$group=="migration policy")]),
              position = position_dodge(width = 0.9), vjust = -0.5) +
    #adjust item labels (size)
    theme(axis.text.x = element_text(size = 12)) +
    #and axis labels (x=group, y=count)
    labs (x="migration policy", y="prop.") +
      scale_y_continuous(limits = c(0, .9)) +
      scale_x_discrete(labels = c("Refugee", "Student", "Migrant")) + 
    scale_fill_manual(values = cb_palette) + 
  #remove legend
    theme(legend.position="none")

# make legend only plot with `flegend` custom function
p4 <- ggplot(data=subset(dat, group=="migration policy"), 
                  aes(x=factor(dat$item[which(dat$group=="migration policy")]), 
                      y=dat$n[which(dat$group=="migration policy")], 
                      fill = factor(dat$outcome[which(dat$group=="migration policy")]))) +
    #add bars (counts)
    geom_bar(stat = "identity", position = "dodge") +
    #and percentage
    geom_text(aes(label = paste0(round(dat$prop[which(dat$group=="migration policy")]*100), "%")),
              position = position_dodge(width = 0.9), vjust = -0.5) +
    #adjust item labels (size)
    theme(axis.text.x = element_text(size = 7)) +
      scale_fill_manual(values = cb_palette) + 
    #and axis labels (x=group, y=count)
    labs (x="migration policy", y="prop.", fill = "Outcome in friendship ties")

legend <- flegend(p4)  

combined_plot <- gridExtra::grid.arrange(p1,p2,p3,legend,
                        nrow = 1)  
 
```


## Sports partners

```{r  fig.width=12, fig.height=8}
#dataframe: outcome counts, per item, nested in groups/themes
dat <- data.frame(group=rep(c("eco-friendly actions", "climate policy", "migration policy" ),each=12),
           item=rep(c("Buying second-hand products", "Minimize item replacement", "Consuming less animal products", "Flight tax", "Meat tax", "Expanding nature reserves", "Annual refugee admissions cap", "Foreign students enrich Dutch universities", "Migrant arrival threatens Dutch culture"),each=4),
           outcome = c("Aware of agreement", "False uniqueness", "False consensus",  "Aware of disagreement"), n=NA)


#subset data of friends
data.1.csn <- data.1[which(data.1$csn==1),]

#counts
{
dat$n[which(dat$item=="Buying second-hand products")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.csn$sechand.self %in% c(1,2) & data.1.csn$sechand.truth %in% c(1,2) & data.1.csn$sechand.perception %in% c(1,2)) | (data.1.csn$sechand.self %in% c(3,4) & data.1.csn$sechand.truth %in% c(3,4) & data.1.csn$sechand.perception %in% c(3,4)))),ifelse(dat$outcome=="False consensus", length(which((data.1.csn$sechand.self %in% c(1,2) & data.1.csn$sechand.truth %in% c(3,4) & data.1.csn$sechand.perception %in% c(1,2)) | (data.1.csn$sechand.self %in% c(3,4) & data.1.csn$sechand.truth %in% c(1,2) & data.1.csn$sechand.perception %in% c(3,4)))),ifelse(dat$outcome=="False uniqueness", length(which((data.1.csn$sechand.self %in% c(1,2) & data.1.csn$sechand.truth %in% c(1,2) & data.1.csn$sechand.perception %in% c(3,4)) | (data.1.csn$sechand.self %in% c(3,4) & data.1.csn$sechand.truth %in% c(3,4) & data.1.csn$sechand.perception %in% c(1,2)))),ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.csn$sechand.self %in% c(1,2) & data.1.csn$sechand.truth %in% c(3,4) & data.1.csn$sechand.perception %in% c(3,4)) | (data.1.csn$sechand.self %in% c(3,4) & data.1.csn$sechand.truth %in% c(1,2) & data.1.csn$sechand.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Consuming less animal products")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.csn$animal.self %in% c(1,2) & data.1.csn$animal.truth %in% c(1,2) & data.1.csn$animal.perception %in% c(1,2)) | (data.1.csn$animal.self %in% c(3,4) & data.1.csn$animal.truth %in% c(3,4) & data.1.csn$animal.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.csn$animal.self %in% c(1,2) & data.1.csn$animal.truth %in% c(3,4) & data.1.csn$animal.perception %in% c(1,2)) | (data.1.csn$animal.self %in% c(3,4) & data.1.csn$animal.truth %in% c(1,2) & data.1.csn$animal.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.csn$animal.self %in% c(1,2) & data.1.csn$animal.truth %in% c(1,2) & data.1.csn$animal.perception %in% c(3,4)) | (data.1.csn$animal.self %in% c(3,4) & data.1.csn$animal.truth %in% c(3,4) & data.1.csn$animal.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.csn$animal.self %in% c(1,2) & data.1.csn$animal.truth %in% c(3,4) & data.1.csn$animal.perception %in% c(3,4)) | (data.1.csn$animal.self %in% c(3,4) & data.1.csn$animal.truth %in% c(1,2) & data.1.csn$animal.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Minimize item replacement")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.csn$replace.self %in% c(1,2) & data.1.csn$replace.truth %in% c(1,2) & data.1.csn$replace.perception %in% c(1,2)) | (data.1.csn$replace.self %in% c(3,4) & data.1.csn$replace.truth %in% c(3,4) & data.1.csn$replace.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.csn$replace.self %in% c(1,2) & data.1.csn$replace.truth %in% c(3,4) & data.1.csn$replace.perception %in% c(1,2)) | (data.1.csn$replace.self %in% c(3,4) & data.1.csn$replace.truth %in% c(1,2) & data.1.csn$replace.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.csn$replace.self %in% c(1,2) & data.1.csn$replace.truth %in% c(1,2) & data.1.csn$replace.perception %in% c(3,4)) | (data.1.csn$replace.self %in% c(3,4) & data.1.csn$replace.truth %in% c(3,4) & data.1.csn$replace.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.csn$replace.self %in% c(1,2) & data.1.csn$replace.truth %in% c(3,4) & data.1.csn$replace.perception %in% c(3,4)) | (data.1.csn$replace.self %in% c(3,4) & data.1.csn$replace.truth %in% c(1,2) & data.1.csn$replace.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Flight tax")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.csn$fly.self %in% c(1,2) & data.1.csn$fly.truth %in% c(1,2) & data.1.csn$fly.perception %in% c(1,2)) | (data.1.csn$fly.self %in% c(3,4) & data.1.csn$fly.truth %in% c(3,4) & data.1.csn$fly.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.csn$fly.self %in% c(1,2) & data.1.csn$fly.truth %in% c(3,4) & data.1.csn$fly.perception %in% c(1,2)) | (data.1.csn$fly.self %in% c(3,4) & data.1.csn$fly.truth %in% c(1,2) & data.1.csn$fly.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.csn$fly.self %in% c(1,2) & data.1.csn$fly.truth %in% c(1,2) & data.1.csn$fly.perception %in% c(3,4)) | (data.1.csn$fly.self %in% c(3,4) & data.1.csn$fly.truth %in% c(3,4) & data.1.csn$fly.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.csn$fly.self %in% c(1,2) & data.1.csn$fly.truth %in% c(3,4) & data.1.csn$fly.perception %in% c(3,4)) | (data.1.csn$fly.self %in% c(3,4) & data.1.csn$fly.truth %in% c(1,2) & data.1.csn$fly.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Meat tax")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.csn$meat.self %in% c(1,2) & data.1.csn$meat.truth %in% c(1,2) & data.1.csn$meat.perception %in% c(1,2)) | (data.1.csn$meat.self %in% c(3,4) & data.1.csn$meat.truth %in% c(3,4) & data.1.csn$meat.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.csn$meat.self %in% c(1,2) & data.1.csn$meat.truth %in% c(3,4) & data.1.csn$meat.perception %in% c(1,2)) | (data.1.csn$meat.self %in% c(3,4) & data.1.csn$meat.truth %in% c(1,2) & data.1.csn$meat.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.csn$meat.self %in% c(1,2) & data.1.csn$meat.truth %in% c(1,2) & data.1.csn$meat.perception %in% c(3,4)) | (data.1.csn$meat.self %in% c(3,4) & data.1.csn$meat.truth %in% c(3,4) & data.1.csn$meat.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.csn$meat.self %in% c(1,2) & data.1.csn$meat.truth %in% c(3,4) & data.1.csn$meat.perception %in% c(3,4)) | (data.1.csn$meat.self %in% c(3,4) & data.1.csn$meat.truth %in% c(1,2) & data.1.csn$meat.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Expanding nature reserves")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.csn$nature.self %in% c(1,2) & data.1.csn$nature.truth %in% c(1,2) & data.1.csn$nature.perception %in% c(1,2)) | (data.1.csn$nature.self %in% c(3,4) & data.1.csn$nature.truth %in% c(3,4) & data.1.csn$nature.perception %in% c(3,4)))),  ifelse(dat$outcome=="False consensus", length(which((data.1.csn$nature.self %in% c(1,2) & data.1.csn$nature.truth %in% c(3,4) & data.1.csn$nature.perception %in% c(1,2)) | (data.1.csn$nature.self %in% c(3,4) & data.1.csn$nature.truth %in% c(1,2) & data.1.csn$nature.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.csn$nature.self %in% c(1,2) & data.1.csn$nature.truth %in% c(1,2) & data.1.csn$nature.perception %in% c(3,4)) | (data.1.csn$nature.self %in% c(3,4) & data.1.csn$nature.truth %in% c(3,4) & data.1.csn$nature.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.csn$nature.self %in% c(1,2) & data.1.csn$nature.truth %in% c(3,4) & data.1.csn$nature.perception %in% c(3,4)) | (data.1.csn$nature.self %in% c(3,4) & data.1.csn$nature.truth %in% c(1,2) & data.1.csn$nature.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Annual refugee admissions cap")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.csn$cap.self %in% c(1,2) & data.1.csn$cap.truth %in% c(1,2) & data.1.csn$cap.perception %in% c(1,2)) | (data.1.csn$cap.self %in% c(3,4) & data.1.csn$cap.truth %in% c(3,4) & data.1.csn$cap.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.csn$cap.self %in% c(1,2) & data.1.csn$cap.truth %in% c(3,4) & data.1.csn$cap.perception %in% c(1,2)) | (data.1.csn$cap.self %in% c(3,4) & data.1.csn$cap.truth %in% c(1,2) & data.1.csn$cap.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.csn$cap.self %in% c(1,2) & data.1.csn$cap.truth %in% c(1,2) & data.1.csn$cap.perception %in% c(3,4)) | (data.1.csn$cap.self %in% c(3,4) & data.1.csn$cap.truth %in% c(3,4) & data.1.csn$cap.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.csn$cap.self %in% c(1,2) & data.1.csn$cap.truth %in% c(3,4) & data.1.csn$cap.perception %in% c(3,4)) | (data.1.csn$cap.self %in% c(3,4) & data.1.csn$cap.truth %in% c(1,2) & data.1.csn$cap.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Foreign students enrich Dutch universities")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.csn$student.self %in% c(1,2) & data.1.csn$student.truth %in% c(1,2) & data.1.csn$student.perception %in% c(1,2)) | (data.1.csn$student.self %in% c(3,4) & data.1.csn$student.truth %in% c(3,4) & data.1.csn$student.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.csn$student.self %in% c(1,2) & data.1.csn$student.truth %in% c(3,4) & data.1.csn$student.perception %in% c(1,2)) | (data.1.csn$student.self %in% c(3,4) & data.1.csn$student.truth %in% c(1,2) & data.1.csn$student.perception %in% c(3,4)))), ifelse(dat$outcome=="False uniqueness", length(which((data.1.csn$student.self %in% c(1,2) & data.1.csn$student.truth %in% c(1,2) & data.1.csn$student.perception %in% c(3,4)) | (data.1.csn$student.self %in% c(3,4) & data.1.csn$student.truth %in% c(3,4) & data.1.csn$student.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.csn$student.self %in% c(1,2) & data.1.csn$student.truth %in% c(3,4) & data.1.csn$student.perception %in% c(3,4)) | (data.1.csn$student.self %in% c(3,4) & data.1.csn$student.truth %in% c(1,2) & data.1.csn$student.perception %in% c(1,2)))), NA ))))

dat$n[which(dat$item=="Migrant arrival threatens Dutch culture")] <- ifelse(dat$outcome=="Aware of agreement", length(which((data.1.csn$threat.self %in% c(1,2) & data.1.csn$threat.truth %in% c(1,2) & data.1.csn$threat.perception %in% c(1,2)) | (data.1.csn$threat.self %in% c(3,4) & data.1.csn$threat.truth %in% c(3,4) & data.1.csn$threat.perception %in% c(3,4)))), ifelse(dat$outcome=="False consensus", length(which((data.1.csn$threat.self %in% c(1,2) & data.1.csn$threat.truth %in% c(3,4) & data.1.csn$threat.perception %in% c(1,2)) | (data.1.csn$threat.self %in% c(3,4) & data.1.csn$threat.truth %in% c(1,2) & data.1.csn$threat.perception %in% c(3,4)))),ifelse(dat$outcome=="False uniqueness", length(which((data.1.csn$threat.self %in% c(1,2) & data.1.csn$threat.truth %in% c(1,2) & data.1.csn$threat.perception %in% c(3,4)) | (data.1.csn$threat.self %in% c(3,4) & data.1.csn$threat.truth %in% c(3,4) & data.1.csn$threat.perception %in% c(1,2)))), ifelse(dat$outcome=="Aware of disagreement", length(which((data.1.csn$threat.self %in% c(1,2) & data.1.csn$threat.truth %in% c(3,4) & data.1.csn$threat.perception %in% c(3,4)) | (data.1.csn$threat.self %in% c(3,4) & data.1.csn$threat.truth %in% c(1,2) & data.1.csn$threat.perception %in% c(1,2)))), NA ))))

}
#fix(dat)
#check
#for (i in unique(dat$item)) {
#  subdat <- dat[which(dat$item==i),]
#  print( sum(subdat$n))
#} ## OKAY

#also add proportion
dat$prop <- dat$n/98

# Define a color blindness friendly palette
cb_palette <- cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73")


#make ggplot object, for items belonging to themes
p1  <- ggplot(data=subset(dat, group=="eco-friendly actions"), 
       aes(x=factor(dat$item[which(dat$group=="eco-friendly actions")]), 
           y=dat$prop[which(dat$group=="eco-friendly actions")], 
           fill = factor(dat$outcome[which(dat$group=="eco-friendly actions")])))+
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = dat$n[which(dat$group=="eco-friendly actions")]),
            position = position_dodge(width = 0.9), vjust = -0.5) +
  theme(axis.text.x = element_text(size = 12)) +
  labs (x="eco-friendly actions", y="prop.") +
  scale_x_discrete(labels = c("Sechand", "Animal", "Replace")) + 
  scale_y_continuous(limits = c(0, .9)) +
  scale_fill_manual(values = cb_palette) + 
  theme(legend.position="none")

p2 <- ggplot(data=subset(dat, group=="climate policy"), 
                  aes(x=factor(dat$item[which(dat$group=="climate policy")]), 
                      y=dat$prop[which(dat$group=="climate policy")], 
                      fill = factor(dat$outcome[which(dat$group=="climate policy")]))) +
    #add bars (counts)
    geom_bar(stat = "identity", position = "dodge") +
    #and percentage
    geom_text(aes(label = dat$n[which(dat$group=="climate policy")]),
              position = position_dodge(width = 0.9), vjust = -0.5) +
    #adjust item labels (size)
    theme(axis.text.x = element_text(size = 12)) +
    #and axis labels (x=group, y=count)
    labs (x="climate policy", y="prop") + 
      scale_y_continuous(limits = c(0, .9)) +
      scale_x_discrete(labels = c("Flight", "Meat", "Nature")) + 
    scale_fill_manual(values = cb_palette) + 
    #remove legend
    theme(legend.position="none")


p3 <- ggplot(data=subset(dat, group=="migration policy"), 
                  aes(x=factor(dat$item[which(dat$group=="migration policy")]), 
                      y=dat$prop[which(dat$group=="migration policy")], 
                      fill = factor(dat$outcome[which(dat$group=="migration policy")]))) +
    #add bars (counts)
    geom_bar(stat = "identity", position = "dodge") +
    #and percentage
    geom_text(aes(label = dat$n[which(dat$group=="migration policy")]),
              position = position_dodge(width = 0.9), vjust = -0.5) +
    #adjust item labels (size)
    theme(axis.text.x = element_text(size = 12)) +
    #and axis labels (x=group, y=count)
    labs (x="migration policy", y="prop.") +
      scale_y_continuous(limits = c(0, .9)) +
      scale_x_discrete(labels = c("Refugee", "Student", "Migrant")) + 
    scale_fill_manual(values = cb_palette) + 
  #remove legend
    theme(legend.position="none")

# make legend only plot with `flegend` custom function
p4 <- ggplot(data=subset(dat, group=="migration policy"), 
                  aes(x=factor(dat$item[which(dat$group=="migration policy")]), 
                      y=dat$n[which(dat$group=="migration policy")], 
                      fill = factor(dat$outcome[which(dat$group=="migration policy")]))) +
    #add bars (counts)
    geom_bar(stat = "identity", position = "dodge") +
    #and percentage
    geom_text(aes(label = paste0(round(dat$prop[which(dat$group=="migration policy")]*100), "%")),
              position = position_dodge(width = 0.9), vjust = -0.5) +
    #adjust item labels (size)
    theme(axis.text.x = element_text(size = 7)) +
      scale_fill_manual(values = cb_palette) + 
    #and axis labels (x=group, y=count)
    labs (x="migration policy", y="prop.", fill = "Outcome in sporting ties")

legend <- flegend(p4)  

combined_plot <- gridExtra::grid.arrange(p1,p2,p3,legend,
                        nrow = 1)  
 
```

# {.unlisted .unnumbered}
